### 2017-09-25 aaV_main.tex
added main file

\documentclass[12pt]{article}

%\textwidth=20cm
%\textheight=16cm
%\setlength{\oddsidemargin}{-1cm}
\pdfoutput=1
\setlength\parindent{0pt}

\usepackage{jheppub}
\usepackage{graphicx,epsfig,amsmath,amssymb,booktabs}
%\usepackage{graphicx,epsfig,amsmath,amssymb}
%\usepackage{multirow,bigdelim,lscape}
%\usepackage{caption}
\usepackage{caption,subcaption}
\usepackage{xspace}

%\usepackage{listings}
%\lstset{basicstyle=\ttfamily}
%% 
%\usepackage{titlesec}

%%% Macros
\newcommand{\eqn}[1]{Eq.~(\ref{#1})}
\newcommand{\ab}{\ensuremath{\alpha_0}}
\newcommand{\als}{\ensuremath{\alpha_s}}
\newcommand{\aapa}{\ensuremath{\gamma\gamma}}
\newcommand{\shortequal}{\ensuremath{\!\!\!=\!\!\!}}
\newcommand{\pT}{\ensuremath{p_\text{T}}}
\newcommand{\order}{\ensuremath{\mathcal{O}}}

\newcommand{\Sherpa}{S\scalebox{0.8}{HERPA}\xspace}
\newcommand{\GoSam}{G\scalebox{0.8}{O}S\scalebox{0.8}{AM}\xspace}
\newcommand{\Recola}{R\scalebox{0.8}{ECOLA}\xspace}
\newcommand{\OpenLoops}{O\scalebox{0.8}{PEN}L\scalebox{0.8}{OOPS	}\xspace}
\newcommand{\QGraf}{QG\scalebox{0.8}{RAF}\xspace}
\newcommand{\FORM}{F\scalebox{0.8}{ORM}\xspace}
\newcommand{\Spinney}{S\scalebox{0.8}{PINNEY}\xspace}
\newcommand{\Ninja}{N\scalebox{0.8}{INJA}\xspace}
\newcommand{\Samurai}{S\scalebox{0.8}{AMURAI}\xspace}
\newcommand{\GolemNF}{G\scalebox{0.8}{OLEM}95\xspace}
\newcommand{\OneLoop}{O\scalebox{0.8}{NE}L\scalebox{0.8}{OOP}\xspace}
\newcommand{\FastJet}{F\scalebox{0.8}{AST}J\scalebox{0.8}{ET}\xspace}

\newcommand{\DIPHOX}{D\scalebox{0.8}{IPHOX}\xspace}
\newcommand{\MCFM}{M\scalebox{0.8}{CFM}\xspace}
\newcommand{\twogammaMC}{2\scalebox{0.8}{gammaMC}\xspace}
\newcommand{\VBFatNLO}{V\scalebox{0.8}{BF@NLO}\xspace}
\newcommand{\RESBOS}{R\scalebox{0.8}{ESBOS}\xspace}

\newcommand{\comment}[1]{\textbf{#1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\begin{frontmatter}

\title{Electroweak corrections to diphoton plus Vector Boson}

\author[a]{Nicolas Greiner,}
\author[a,b]{Marek Sch\"onherr}

\affiliation[a]{Physik Institut, Universit{\"a}t Z{\"u}rich, Winterthurerstr.190, 8057 Z\"urich, Switzerland}
\affiliation[b]{CERN}

\preprint{
  \small
  \begin{flushright}
    ZU--TH 
  \end{flushright}
}

\abstract{
  We calculate the next-to-leading order electroweak corrections...
}

\keywords{EW corrections, Photon, NLO, Jets}

\begin{document}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Introduction
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Calculational Setup
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Calculational setup}
\label{sec:setup}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Results
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Conclusions
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
\label{sec:conclusions}

\section*{Acknowledgements}
N.G.\ was supported by the Swiss National Science Foundation under contract
PZ00P2\_154829. M.S.\ was supported by PITN--GA--2012--315877 ({\it MCnet}) 
and the ERC Advanced Grant MC@NNLO (340983).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\providecommand{\href}[2]{#2}\begingroup\raggedright\begin{thebibliography}{100}

\end{thebibliography}\endgroup

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-10-03 conclusions.tex
restructured

\section{Conclusions}
\label{sec:conclusions}

We did good.

### 2017-10-03 intro.tex
restructured

\section{Introduction}
\label{sec:intro}

We love to calculate things that are important.
\cite{Gleisberg:2008ta}

### 2017-10-03 results.tex
restructured

\section{Results}
\label{sec:results}

We got those results.

### 2017-10-03 setup.tex
restructured

\section{Calculational setup}
\label{sec:setup}

We do it in a way that works.

### 2017-10-04 aaV_main.tex
restructured
added a few diagrams

@@
 
-\title{Electroweak corrections to diphoton plus Vector Boson}
+\title{NLO QCD+EW corrections to diphoton production in association with a vector boson}
 
@@
   \begin{flushright}
-    ZU--TH 
+    ZU--TH--??, CERN-- 
   \end{flushright}
@@
 
+\hypersetup{
+  pdftitle = {NLO QCD+EW corrections to diphoton production in association with a vector boson},
+  pdfauthor = {Nicolas Greiner, Marek Schoenherr}
+}
+
 \begin{document}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
+\input{intro}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Calculational setup}
-\label{sec:setup}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\input{setup}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\input{results}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\input{results}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusions}
-\label{sec:conclusions}
+\input{conclusions}
 
@@
 
-\providecommand{\href}[2]{#2}\begingroup\raggedright\begin{thebibliography}{100}
-
-\end{thebibliography}\endgroup
+\bibliographystyle{amsunsrt_mod}
+\bibliography{journal}
 

### 2017-10-04 setup.tex
added a few diagrams

@@
 We do it in a way that works.
+
+\begin{figure}[t!]
+  \begin{tabular}{ccccc}
+    \includegraphics[width=0.3\textwidth]{diagrams/aaa_V_1} & &
+    \includegraphics[width=0.3\textwidth]{diagrams/aaa_V_2} & &
+    \includegraphics[width=0.3\textwidth]{diagrams/aaa_V_3} \\
+  \end{tabular}
+  \caption{
+    Sample diagrams of electroweak virtual corrections to triple 
+    photon production.
+  }
+\end{figure}
+
+\begin{figure}[t!]
+  \begin{tabular}{ccccc}
+%     \includegraphics[width=0.3\textwidth]{diagrams/aaW_V_1} & &
+%     \includegraphics[width=0.3\textwidth]{diagrams/aaW_V_2} & &
+%     \includegraphics[width=0.3\textwidth]{diagrams/aaW_V_3} \\
+  \end{tabular}
+  \caption{
+    Sample diagrams of electroweak virtual corrections to diphoton 
+    production in association with a lepton-neutrino pair.
+  }
+\end{figure}
+
+\begin{figure}[t!]
+  \begin{tabular}{ccccc}
+%     \includegraphics[width=0.3\textwidth]{diagrams/aaZ_V_1} & &
+%     \includegraphics[width=0.3\textwidth]{diagrams/aaZ_V_2} & &
+%     \includegraphics[width=0.3\textwidth]{diagrams/aaZ_V_3} \\
+  \end{tabular}
+  \caption{
+    Sample diagrams of electroweak virtual corrections to diphoton 
+    production in association with a lepton-pair.
+  }
+\end{figure}

### 2017-10-06 setup.tex
added more diagrams

--- 2017-10-03 setup.tex
@@
 We do it in a way that works.
+
+\begin{figure}[t!]
+  \begin{tabular}{ccccc}
+    \includegraphics[width=0.288\textwidth]{diagrams/aaa_V_2} & &
+    \includegraphics[width=0.288\textwidth]{diagrams/aaa_V_1} & &
+    \includegraphics[width=0.288\textwidth]{diagrams/aaa_V_3} \\
+  \end{tabular}
+  \caption{
+    Sample diagrams of electroweak virtual corrections to triple 
+    photon production.
+  }
+\end{figure}
+
+\begin{figure}[t!]
+  \begin{tabular}{ccccc}
+    \includegraphics[width=0.288\textwidth]{diagrams/aaW_V_2} & &
+    \includegraphics[width=0.288\textwidth]{diagrams/aaW_V_1} & &
+    \includegraphics[width=0.288\textwidth]{diagrams/aaW_V_3} \\
+  \end{tabular}
+  \caption{
+    Sample diagrams of electroweak virtual corrections to diphoton 
+    production in association with a lepton-neutrino pair.
+  }
+\end{figure}
+
+\begin{figure}[t!]
+  \begin{tabular}{ccccc}
+    \includegraphics[width=0.288\textwidth]{diagrams/aaZ_V_2} & &
+    \includegraphics[width=0.288\textwidth]{diagrams/aaZ_V_1} & &
+    \includegraphics[width=0.288\textwidth]{diagrams/aaZ_V_3} \\
+  \end{tabular}
+  \caption{
+    Sample diagrams of electroweak virtual corrections to diphoton 
+    production in association with a lepton-pair.
+  }
+\end{figure}

### 2017-10-17 results.tex
aaa plots in draft, need refinement

@@
 We got those results.
+
+We calculate $\mathrm{B}(\muF)$, $\deltaQCD(\muR,\muF)$ and 
+$\deltaEW(\muF^0)$
+
+\subsection{\texorpdfstring{$\boldsymbol pp\to \gamma\gamma\gamma$}{pp->aaa}}
+
+\begin{figure}[t!]
+  \centering
+  \includegraphics[width=0.32\textwidth]{figs_aaa/pT_y1}
+  \includegraphics[width=0.32\textwidth]{figs_aaa/pT_y2}
+  \includegraphics[width=0.32\textwidth]{figs_aaa/pT_y3}
+  \caption{
+    Transverse momentum of the leading (left), subleading (centre) 
+    and third leading (right) photon at the LHC at 13\,TeV.
+    \label{fig:aaa:pt}
+  }
+\end{figure}
+
+\begin{figure}[t!]
+  \centering
+  \includegraphics[width=0.32\textwidth]{figs_aaa/m_y1y2_comb_log}
+  \includegraphics[width=0.32\textwidth]{figs_aaa/m_y1y3_comb_log}
+  \includegraphics[width=0.32\textwidth]{figs_aaa/m_y2y3_comb_log}
+  \caption{
+    Pairwise invariant mass of the leading and subleading photon (left),
+    leading and third leading photon (centre), subleading and third leading 
+    photon (right) at the LHC at 13\,TeV.\\
+    \comment{MS: Spike in $m_{\gamma_1\gamma_2}$ is in NLO \QCDtEW 
+             and comes from $\deltaEW\approx 10$ in this bin at the 
+             edge of the LO phase space.}
+    \label{fig:aaa:myy}
+  }
+\end{figure}

### 2017-10-17 results.tex
added comments for aaa description

@@
 
-\subsection{\texorpdfstring{$\boldsymbol pp\to \gamma\gamma\gamma$}{pp->aaa}}
+\subsection{\texorpdfstring{$\boldsymbol{\gamma\gamma\gamma}$}{aaa} production}
+\label{sec:results:aaa}
 
@@
 \end{figure}
+
+\begin{itemize}
+  \item \pT of 3rd photon much softer than 1st and 2nd
+  \item EW corrections to \pT of 1st and 2nd photon nearly identical and 
+        $\approx -10\%$ at 500\,GeV, 3rd photon almost twice that.
+  \item in all cases NLO EW outside LO uncertainty band
+  \item NLO QCD dominated by real corrections, i.e.\ additional 
+        jet emissions
+  \item intensified through opening of new $qg$ channels and large 
+        gluon luminosity
+  \item can be controlled in fixed-order calculations through jet veto, 
+        needs proper multijet merging
+  \item because at LO the leading jet needs to be in the opposite 
+        hemisphere as the subleading and third leading jet, 
+        $m_{\gamma_1\gamma_2}$ and $m_{\gamma_1\gamma_3}$ 
+        exhibit kinematic edges at LO
+  \item kinematic conditions relaxed at NLO (both QCD and EW, 
+        but QCD dominating), large corrections around those edges, 
+        leads to artifacts in multiplicative combination
+  \item NLO QCD very similar for $m_{\gamma_1\gamma_2}$ and 
+	$m_{\gamma_1\gamma_3}$, $m_{\gamma_2\gamma_3}$ with interesting 
+	structure around 80-90\,GeV
+  \item $m_{\gamma_1\gamma_2}$ again exhibits small excess at $2m_W$
+  \item small positive EW corrections at small $m_{\gamma\gamma}$ 
+  \item $\approx -10\%$ at 1\,TeV for all $m_{\gamma\gamma}$ 
+  \item NLO EW very similar for all $m_{\gamma\gamma}$ 
+\end{itemize}
+
+\subsection{\texorpdfstring{$\boldsymbol{\gamma\gamma\ell^+\ell^-}$}{aall} production}
+\label{sec:results:aaz}
+
+\subsection{\texorpdfstring{$\boldsymbol{\gamma\gamma\ell\nu}$}{aalnu} production}
+\label{sec:results:aaw}
+
+\comment{MS: is that $\ell^+$ or $\ell^-$?}

### 2017-10-17 intro.tex
update intro and merge

@@
 
-We love to calculate things that are important.
-\cite{Gleisberg:2008ta}
+The precise understanding of the electroweak symmetry breaking mechanism is an important cornerstone in verifying the
+Standard Model. Different realizations of the electroweak sector or new physics coupling to electroweak gauge bosons will
+yield to deviations compared to the Standard Model prediction. New physics effects can conveniently be described in terms
+of an effective theory where new heavy degrees of freedom are integrated out and deviations from the Standard Model are 
+parametrised by higher dimensional operators \cite{Weinberg:1978kz,Weinberg:1979pi}. Higher dimensional operators can lead
+ to deviations in triple and quartic gauge couplings. Moreover, new vertices (e.g. $Z\gamma\gamma$) that do not exist in the 
+Standard Model can appear. The class of processes that involve a pair of photons in association with another vector boson
+allows to measure deviations in triple and quartic gauge couplings and is therefore a particularly interesting class of processes.
+ Consequently both ATLAS and CMS have measured these type of processes und derived constraints on anomalous gauge
+ couplings \cite{Aad:2016sau,Sirunyan:2017lvq,Aad:2015uqa,Aad:2015bua}

### 2017-10-17 intro.tex
update intro, added some ref

@@
  Consequently both ATLAS and CMS have measured these type of processes und derived constraints on anomalous gauge
- couplings \cite{Aad:2016sau,Sirunyan:2017lvq,Aad:2015uqa,Aad:2015bua}
+ couplings \cite{Aad:2016sau,Sirunyan:2017lvq,Aad:2015uqa,Aad:2015bua}.\\
+ In this paper we calculate the next-to-leading order QCD and electroweak corrections to the processes 
+ $\gamma\gamma\gamma$, $\gamma\gamma e^{+} e^{-}$ and $\gamma\gamma e^{-} \bar{\nu_e}$. For the latter two, all
+ possible off-shell contributions are taken into account. The QCD corrections to these processes are already known 
+ \cite{Bozzi:2011en,Campbell:2012ft,Bozzi:2011wwa}. For a more complete picture of the higher order effects we also
+% recalculate the QCD corrections for a center of mass energy of $13$ TeV, and supplement them with the 
+% next-to-leading order electroweak corrections.

### 2017-10-18 intro.tex
update setup

@@
  \cite{Bozzi:2011en,Campbell:2012ft,Bozzi:2011wwa}. For a more complete picture of the higher order effects we also
-% recalculate the QCD corrections for a center of mass energy of $13$ TeV, and supplement them with the 
-% next-to-leading order electroweak corrections.
+recalculate the QCD corrections for a center of mass energy of $13$ TeV, and supplement them with the 
+ next-to-leading order electroweak corrections. Although the electroweak corrections are much smaller at the level
+ of the total cross section compared to the NLO QCD corrections they are particularly important when deriving limits on 
+ anomalous couplings. The effects of higher dimensional operators increase in the high energy tails of differential distributions
+ and lead to a change of the shapes. And it is in the same region where the Sudakov logarithms from the electroweak
+ corrections will play an essential role as well.\\
+ The paper is organized as follows. In section \ref{sec:setup} we describe the calculational setup that has been used to obtain our
+ numerical result which we are going to discuss in section \ref{sec:results} before we conclude in section \ref{sec:conclusions}.

### 2017-10-18 setup.tex
aaa plots in draft, need refinement
update setup

@@
 \label{sec:setup}
+The results presented in this paper have been obtained by combining the two tools
+\GoSam~\cite{Cullen:2011ac,Cullen:2014yla} and \Sherpa~\cite{Gleisberg:2008ta}
+which allows for a fully automated calculation of cross section and observables and next-to-leading order in QCD as well
+as in the electroweak coupling.
+\GoSam is a package which generates the code for the numerical evaluation of
+the one loop scattering amplitudes starting from the Feynman diagrams,
+generated with \QGraf~\cite{Nogueira:1991ex} and further processed with
+\FORM~\cite{Vermaseren:2000nd,Kuipers:2012rf} and
+\Spinney~\cite{Cullen:2010jv} to perform necessary algebraic
+manipulations to obtain an optimized expression for the matrix elements.
+For the integrand reduction of the diagrams we use the \Ninja
+library~\cite{Peraro:2014cba}, an implementation of the technique of integrand
+reduction via Laurent expansion~\cite{Mastrolia:2012bu,vanDeurzen:2013saa}.
+Alternatively one can choose other reduction strategies such as OPP reduction
+method~\cite{Ossola:2006us,Mastrolia:2008jb,Ossola:2008xq} which is
+implemented in $d$ dimensions in \Samurai~\cite{Mastrolia:2010nb}, or methods based on
+tensor integral reduction as implemented in
+\GolemNF~\cite{Heinrich:2010ax,Binoth:2008uq,Cullen:2011kv,Guillet:2013msa}.
+We have used \OneLoop~\cite{vanHameren:2010cp} to evaluate the scalar integrals.
 
-We do it in a way that works.
+We define our central scales through
+\begin{equation}
+  \label{eq:murfdef}
+  \begin{split}
+    \muR^0 = \muF^0 = \ldots
+  \end{split}
+\end{equation}
+and subsequently vary them by the conventional factor 
+of two to estimate higher order contributions.
 

### 2017-10-18 results.tex
link to text
update setup
update aaa figs

@@
     Transverse momentum of the leading (left), subleading (centre) 
-    and third leading (right) photon at the LHC at 13\,TeV.
+    and third leading (right) photon 
+    in triple photon production at the LHC at 13\,TeV. 
+    The distributions are shown at LO (blue), NLO QCD (green), 
+    NLO EW (orange), NLO \QCDpEW\ (red) and NLO \QCDtEW\ (black) 
+    including scale uncertainties. The top ratio plot details 
+    the relative corrections to the leading order cross section 
+    without applying any jet veto, while the centre ratio plot 
+    applies a jet veto of $p_\mathrm{T}^\mathrm{veto}=\text{30\,GeV}$. 
+    The lower ratio highlights the size of the electroweak corrections.
     \label{fig:aaa:pt}
@@
     leading and third leading photon (centre), subleading and third leading 
-    photon (right) at the LHC at 13\,TeV.\\
-    \comment{MS: Spike in $m_{\gamma_1\gamma_2}$ is in NLO \QCDtEW 
+    photon (right) 
+    in triple photon production at the LHC at 13\,TeV. 
+    Details as in Fig.\ \ref{fig:aaa:pt}.\\
+    \comment{MS: Spike in $m_{\gamma_1\gamma_2}$ is in NLO \QCDtEW\ 
              and comes from $\deltaEW\approx 10$ in this bin at the 
@@
     \label{fig:aaa:myy}
+  }
+\end{figure}
+
+\begin{figure}[t!]
+  \centering
+  \includegraphics[width=0.32\textwidth]{figs_aaa/dphi_y1y2}
+  \includegraphics[width=0.32\textwidth]{figs_aaa/dphi_y1y3}
+  \includegraphics[width=0.32\textwidth]{figs_aaa/dphi_y2y3}
+  \caption{
+    Azimuthal separation of the leading and subleading photon (left),
+    leading and third leading photon (centre), subleading and third leading 
+    photon (right) 
+    in triple photon production at the LHC at 13\,TeV. 
+    Details as in Fig.\ \ref{fig:aaa:pt}.\\
+    \comment{MS: Spike in $\Delta\phi_{\gamma_2\gamma_3}$ is in NLO \QCDtEW\ 
+             and comes from $\deltaEW\approx 2$ in this bin at the 
+             edge of the LO phase space.}
+    \label{fig:aaa:dphi}
   }
@@
 
-\subsection{\texorpdfstring{$\boldsymbol{\gamma\gamma\ell^+\ell^-}$}{aall} production}
-\label{sec:results:aaz}
-
 \subsection{\texorpdfstring{$\boldsymbol{\gamma\gamma\ell\nu}$}{aalnu} production}
@@
 \comment{MS: is that $\ell^+$ or $\ell^-$?}
+
+\begin{figure}[t!]
+  \centering
+  \includegraphics[width=0.32\textwidth]{figs_aaw/pT_y1}
+  \includegraphics[width=0.32\textwidth]{figs_aaw/pT_y2}
+  \includegraphics[width=0.32\textwidth]{figs_aaw/pT_l1}
+  \caption{
+    Transverse momentum of the leading (left), subleading (centre) 
+    and third leading (right) photon at the LHC at 13\,TeV.
+    \label{fig:aaw:pt}
+  }
+\end{figure}
+
+\begin{figure}[t!]
+  \centering
+  \includegraphics[width=0.32\textwidth]{figs_aaw/m_y1y2_comb_log}
+  \includegraphics[width=0.32\textwidth]{figs_aaw/m_y1l1_comb_log}
+  \caption{
+    Pairwise invariant mass of the leading and subleading photon (left),
+    leading and third leading photon (centre), subleading and third leading 
+    photon (right) at the LHC at 13\,TeV.\\
+    \comment{MS: Spike in $m_{\gamma_1\gamma_2}$ is in NLO \QCDtEW 
+             and comes from $\deltaEW\approx 10$ in this bin at the 
+             edge of the LO phase space.}
+    \label{fig:aaw:myy}
+  }
+\end{figure}
+
+\begin{figure}[t!]
+  \centering
+  \includegraphics[width=0.32\textwidth]{figs_aaw/dphi_y1_y2}
+  \includegraphics[width=0.32\textwidth]{figs_aaw/dphi_y1_l1}
+  \includegraphics[width=0.32\textwidth]{figs_aaw/dphi_y2_l1}
+  \caption{
+    Azimuthal separation of the leading and subleading photon (left),
+    leading and third leading photon (centre), subleading and third leading 
+    photon (right) at the LHC at 13\,TeV.\\
+    \comment{MS: Spike in $m_{\gamma_1\gamma_2}$ is in NLO \QCDtEW 
+             and comes from $\deltaEW\approx 10$ in this bin at the 
+             edge of the LO phase space.}
+    \label{fig:aaw:dphi}
+  }
+\end{figure}
+
+\subsection{\texorpdfstring{$\boldsymbol{\gamma\gamma\ell^+\ell^-}$}{aall} production}
+\label{sec:results:aaz}
+
+\begin{figure}[t!]
+  \centering
+  \includegraphics[width=0.32\textwidth]{figs_aaz/pT_y1}
+  \includegraphics[width=0.32\textwidth]{figs_aaz/pT_y2}
+  \includegraphics[width=0.32\textwidth]{figs_aaz/pT_l1l2_comb_log}
+  \caption{
+    Transverse momentum of the leading (left) and subleading (centre) 
+    photon as well as the dressed lepton pair (right) 
+    in diple photon production in association with a lepton pair 
+    at the LHC at 13\,TeV. 
+    Details as in Fig.\ \ref{fig:aaa:pt}.
+    \label{fig:aaz:pt}
+  }
+\end{figure}
+
+\begin{figure}[t!]
+  \centering
+  \includegraphics[width=0.32\textwidth]{figs_aaz/m_y1y2_comb_log}
+  \includegraphics[width=0.32\textwidth]{figs_aaz/m_y1l1l2_comb_log}
+  \includegraphics[width=0.32\textwidth]{figs_aaz/m_y2l1l2_comb_log}
+  \caption{
+    Pairwise invariant mass of the leading and subleading photon (left),
+    the leading photon and the lepton pair (centre), and the subleading 
+    photon and the lepton pair (right)
+    in diple photon production in association with a lepton pair 
+    at the LHC at 13\,TeV. 
+    Details as in Fig.\ \ref{fig:aaa:pt}.\\
+    \comment{MS: Spike in $m_{\gamma_1\ell_1\ell_2}$ is in NLO \QCDtEW\ 
+             and comes from $\deltaEW\approx 10$ in this bin at the 
+             edge of the LO phase space.}
+    \label{fig:aaz:myy}
+  }
+\end{figure}
+
+\begin{figure}[t!]
+  \centering
+  \includegraphics[width=0.32\textwidth]{figs_aaz/dphi_y1_y2}
+  \includegraphics[width=0.32\textwidth]{figs_aaz/dphi_y1_l1l2}
+  \includegraphics[width=0.32\textwidth]{figs_aaz/dphi_y2_l1l2}
+  \caption{
+    Azimuthal separation of the leading and subleading photon (left),
+    the leading photon and the lepton pair (centre), and the subleading 
+    photon and the lepton pair (right)
+    in diple photon production in association with a lepton pair 
+    at the LHC at 13\,TeV. 
+    Details as in Fig.\ \ref{fig:aaa:pt}.\\
+    \comment{MS: Spike in $\Delta\phi_{\gamma_1,\ell_1\ell_2}$ is in NLO \QCDtEW\ 
+             and comes from $\deltaEW\approx 10$ in this bin at the 
+             edge of the LO phase space.}
+    \label{fig:aaz:dphi}
+  }
+\end{figure}

### 2017-10-19 results.tex
few mods

@@
     without applying any jet veto, while the centre ratio plot 
-    applies a jet veto of $p_\mathrm{T}^\mathrm{veto}=\text{30\,GeV}$. 
+    applies a jet veto of $p_\mathrm{T,jet}^\mathrm{veto}=\text{30\,GeV}$. 
     The lower ratio highlights the size of the electroweak corrections.
@@
   \includegraphics[width=0.32\textwidth]{figs_aaw/m_y1l1_comb_log}
+  \includegraphics[width=0.32\textwidth]{figs_aaw/m_t_comb_log}
   \caption{

### 2017-10-19 intro.tex
updates

--- 2017-10-17 intro.tex
@@
 
-The precise understanding of the electroweak symmetry breaking mechanism is an important cornerstone in verifying the
-Standard Model. Different realizations of the electroweak sector or new physics coupling to electroweak gauge bosons will
-yield to deviations compared to the Standard Model prediction. New physics effects can conveniently be described in terms
-of an effective theory where new heavy degrees of freedom are integrated out and deviations from the Standard Model are 
-parametrised by higher dimensional operators \cite{Weinberg:1978kz,Weinberg:1979pi}. Higher dimensional operators can lead
- to deviations in triple and quartic gauge couplings. Moreover, new vertices (e.g. $Z\gamma\gamma$) that do not exist in the 
-Standard Model can appear. The class of processes that involve a pair of photons in association with another vector boson
-allows to measure deviations in triple and quartic gauge couplings and is therefore a particularly interesting class of processes.
- Consequently both ATLAS and CMS have measured these type of processes und derived constraints on anomalous gauge
- couplings \cite{Aad:2016sau,Sirunyan:2017lvq,Aad:2015uqa,Aad:2015bua}
+The precise understanding of the electroweak symmetry breaking 
+mechanism is an important cornerstone of the LHC physics 
+programme. 
+Different realisations of the electroweak sector or new physics 
+coupling to electroweak gauge bosons will yield to deviations 
+compared to the Standard Model prediction. 
+New physics effects can conveniently be described in terms of 
+an effective theory where new heavy degrees of freedom are 
+integrated out and deviations from the Standard Model are 
+parametrised by higher dimensional operators 
+\cite{Weinberg:1978kz,Weinberg:1979pi}. 
+Higher dimensional operators can lead to deviations in triple 
+and quartic gauge couplings. Moreover, new vertices 
+(e.g. $\gamma\gamma\gamma$, $Z\gamma\gamma$) that do not 
+exist in the Standard Model can appear. 
+The class of processes that involve a pair of photons in 
+association with another vector boson allows to measure 
+deviations in triple and quartic gauge couplings and is 
+therefore a particularly interesting class of processes. 
+Consequently both ATLAS and CMS have measured these types of 
+processes and derived constraints on anomalous gauge couplings 
+\cite{Aad:2016sau,Sirunyan:2017lvq,Aad:2015uqa,Aad:2015bua}.
+
+In this paper we calculate the next-to-leading order QCD and 
+electroweak corrections to the processes $\gamma\gamma\gamma$, 
+$\gamma\gamma e^{+} e^{-}$ and $\gamma\gamma e^{-} \bar{\nu_e}$. 
+For the latter two, all possible off-shell contributions of 
+intermediate vector bosons are taken into account. 
+The QCD corrections to these processes have already appeared 
+in the literature 
+\cite{Bozzi:2011en,Campbell:2012ft,Bozzi:2011wwa}. 
+For a more complete picture of the higher order effects we 
+recompute them for a centre of mass energy of 
+13\,TeV, and supplement them with the next-to-leading order 
+electroweak corrections. 
+Although the electroweak corrections are much smaller at the level 
+of the total cross section compared to the NLO QCD corrections 
+they are particularly important when deriving limits on 
+anomalous couplings. 
+The effects of higher dimensional operators increase in the 
+high energy tails of differential distributions and lead to a 
+change of the shapes. And it is in the same region where the 
+Sudakov logarithms from the electroweak corrections will play 
+an essential role as well.
+
+The paper is organized as follows. 
+In Section \ref{sec:setup} we describe the calculational setup 
+that has been used to obtain our numerical result which we are 
+going to discuss in Section \ref{sec:results} before we 
+conclude in Section \ref{sec:conclusions}.

### 2017-10-19 results.tex
updates

@@
 \label{sec:results}
+
+We use the \textsc{CT14nlo} PDF set with $\alpha_s(m_Z)=0.118$. 
+The use of a QCD-only PDF is justified by the fact that, 
+at LO, the photon induced corrections are negligible.
+
+We define our central scales through
+\begin{equation}
+  \label{eq:murfdef}
+  \begin{split}
+    \muR^0 = \muF^0 = \ldots
+  \end{split}
+\end{equation}
+and subsequently vary them by the conventional factor 
+of two to estimate higher order contributions.
 
@@
 $\deltaEW(\muF^0)$
+
+\begin{table}[h!]
+  \centering
+  \begin{tabular}{l||c|c|c}
+      & $\;\;pp \to \gamma \gamma\gamma\;\;$
+      & $\;\;pp \to \gamma \gamma e^-\bar\nu_e\;\;$ 
+      & $\;\;pp \to \gamma \gamma e^+e^-\;\;$ \\
+    \hline\hline
+    $\sigma_\text{LO}\;\;[\text{pb}] $ &  &  & \\
+    \hline
+    $\delta_\text{QCD}\;\;[\text{pb}]\;\;\pTveto=\infty $ &  &  & \\
+    \hline
+    $\delta_\text{QCD}\;\;[\text{pb}]\;\;\pTveto=30\,\text{GeV} $ &  &  & \\
+    \hline
+    $\delta_\text{EW}\;\;[\text{pb}] $ &  &  & \\
+  \end{tabular}
+  \caption{
+    Total cross sections at LO, NLO QCD and NLO EW for $\gamma\gamma\gamma$, 
+    $\gamma\gamma e^-\bar\nu_e$ and $\gamma\gamma e^+e^-$
+    production at 13\,TeV at the LHC.
+    \label{tab:xsec}
+  } 
+\end{table}
 

### 2017-10-19 setup.tex
updates

@@
 
-We define our central scales through
-\begin{equation}
-  \label{eq:murfdef}
-  \begin{split}
-    \muR^0 = \muF^0 = \ldots
-  \end{split}
-\end{equation}
-and subsequently vary them by the conventional factor 
-of two to estimate higher order contributions.
+A selection of one-loop amplitudes contributing to the three 
+considered processes are shown in Figures 
+\ref{fig:aaa:amps}--\ref{fig:aaz:amps}. 
+The highest point loop integrals occuring in $\gamma\gamma\gamma$ 
+production are pentagons, while both $\gamma\gamma e^-\bar\nu_e$ 
+and $\gamma\gamma e^+e^-$ productions include up to hexagons at 
+NLO EW.
 
@@
     photon production.
+    \label{fig:aaa:amps}
   }
@@
     production in association with a lepton-neutrino pair.
+    \label{fig:aaw:amps}
   }
@@
     production in association with a lepton-pair.
+    \label{fig:aaz:amps}
   }
 \end{figure}
+
+\Sherpa, on the other hand, provides the tree-level matrix 
+elements, infrared subtraction, process management and phase-space 
+integration of all contributions to all processes considered in 
+this publication through its tree-level matrix element generator 
+\textsc{Amegic} \cite{Krauss:2001iv}. 
+Its inbuilt infrared subtraction is performed in the QED 
+generalisation of the Catani-Seymour scheme~\cite{Catani:1996vz,
+  Dittmaier:1999mb,Gleisberg:2007md,Kallweit:2014xda,
+  Kallweit:2015dum,Kallweit:2017khh,Schonherr:2017xxx}
+and includes the appropriate initial state mass factorisation 
+counter terms.
+Both programs, \Sherpa and \GoSam, are interfaced through a 
+dedicated interface based on the 
+Binoth Les Houches Accord~\cite{Binoth:2010xt,Alioli:2013nda}. 
+Cross-checks of the tree-level matrix elements of \GoSam and 
+\Sherpa and the renormalized pole coefficients of the virtual 
+corrections of \GoSam and the infrared poles of \Sherpa have 
+been performed for several phase space points spanning 
+multiple kinematic regimes and we have found excellent 
+agreement.
+
+This combination of tools was previously used to calculate the 
+NLO QCD corrections to \ldots \cite{} and the 
+NLO EW corrections to for $\gamma\gamma+0,1,2\,\text{jets}$ production 
+in \cite{Chiesa:2017gqx}.

### 2017-10-19 results.tex
relative aa contrib

@@
 \label{sec:results}
+
+In this section we present numerical results for the NLO QCD and NLO EW 
+corrections in the production of 
+(at least) two 
+isolated photons, both inclusively and in association with at least one 
+or two jets, $\text{pp}\to \gamma\gamma+0,1,2\,\text{jets}$ at the 
+LHC at a centre-of-mass energy of 13\,TeV. 
+Our calculation is performed in the Standard Model using the complex-mass 
+scheme with the following input parameters
+\begin{center}
+  \begin{tabular}{rclrcl}
+    $\alpha(0)$ &\shortequal& $1/137.03599976$  \qquad &&& \\
+    $m_W$ &\shortequal& $80.385\; \text{GeV}$       & $\Gamma_W$ &\shortequal& $2.085\; \text{GeV}$ \\
+    $m_Z$ &\shortequal& $91.1876\; \text{GeV}$      & $\Gamma_Z$ &\shortequal& $2.4952\; \text{GeV}$ \\
+%     $m_h$ &\shortequal& $125.0\; \text{GeV}$        & $\Gamma_h$ &\shortequal& $0$\\
+    $m_t$ &\shortequal& $171.2\; \text{GeV}$        & $\Gamma_t$ &\shortequal& $0$\;.
+  \end{tabular}
+\end{center}
+The width of the top quark can be safely neglected as there are no 
+diagrams containing it as an $s$-channel resonance which can potentially 
+go on-shell. 
+At the same time there are no diagrams 
+containing the Higgs boson due to the absence of $W$, $Z$ or top quark 
+propagators at LO.
+All other parton masses and widths are set to zero, i.e.\ we are working 
+in the five-flavour scheme.
 
@@
 \end{figure}
+
+\begin{figure}[t!]
+  \setlength{\unitlength}{\textwidth}
+  \begin{picture}(0,1)
+    \put(0,0.24){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/pT_y1}}
+    \put(0,0.12){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/pT_y2}}
+    \put(0,0){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/pT_l1l2_comb_log}}
+    \put(0.33,0.24){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/m_y1y2_comb_log}}
+    \put(0.33,0.12){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/m_y1l1l2_comb_log}}
+    \put(0.33,0){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/m_y2l1l2_comb_log}}
+    \put(0.66,0.24){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/dphi_y1_y2}}
+    \put(0.66,0.12){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/dphi_y1_l1l2}}
+    \put(0.66,0){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/dphi_y2_l1l2}}
+  \end{picture}
+  \caption{
+    Contribution of $\gamma\gamma$-induced production channels at LO.
+    \label{fig:aaz:aa-ind}
+  }
+\end{figure}

### 2017-10-20 results.tex
updates to results

--- 2017-10-19 results.tex
@@
 
-We use the \textsc{CT14nlo} PDF set with $\alpha_s(m_Z)=0.118$. 
+In this section we present numerical results for the NLO QCD and NLO EW 
+corrections to all three production processes of a diphoton pair in 
+association with a third vector boson, a third photon, a $W$ or a $Z$ 
+boson, at the LHC at a centre-of-mass energy of 13\,TeV. 
+In case of an accompanying $W$ or a $Z$ boson, we consider the full 
+off-shell leptonic final state, i.e.\ lepton-neutrino or lepton-pair 
+production.
+All results are obtained in the Standard Model using the complex-mass 
+scheme \cite{Denner:2005fg} with the following input parameters
+\begin{center}
+  \begin{tabular}{rclrcl}
+    $\alphazero$ &\shortequal& $1/137.03599976$  \qquad &&& \\
+    $G_\mu$ &\shortequal& $1.1663787\times 10^{-5}\; \text{GeV}^2$ &&& \\
+    $m_W$ &\shortequal& $80.385\; \text{GeV}$       & $\Gamma_W$ &\shortequal& $2.085\; \text{GeV}$ \\
+    $m_Z$ &\shortequal& $91.1876\; \text{GeV}$      & $\Gamma_Z$ &\shortequal& $2.4952\; \text{GeV}$ \\
+    $m_h$ &\shortequal& $125.0\; \text{GeV}$        & $\Gamma_h$ &\shortequal& $0$\\
+    $m_t$ &\shortequal& $173.2\; \text{GeV}$        & $\Gamma_t$ &\shortequal& $0$\;.
+  \end{tabular}
+\end{center}
+Both the width of the top quark and the Higgs boson can safely be 
+neglected as there are no diagrams containing either as $s$-channel 
+propagators which can potentially go on-shell. 
+All other lepton and parton masses and widths are set to zero, 
+i.e.\ we are working in the five-flavour scheme.
+We use the \textsc{CT14nlo} PDF set with $\alphas(m_Z)=0.118$. 
 The use of a QCD-only PDF is justified by the fact that, 
-at LO, the photon induced corrections are negligible.
+at LO, the photon induced corrections are either non-existant 
+(\aaa, \aaw) or negligible (\aaz).
+This finding will be detailed in Section \ref{sec:results:aaz}.
 
@@
   \begin{split}
-    \muR^0 = \muF^0 = \ldots
+    \muR^0 = \muF^0 = \left\{
+    \begin{array}{ll}
+      m_{\aaa} \qquad & \text{in \aaa\ production} \\[2mm]
+      \tfrac{1}{2}\,H_T' & \text{in \aaw\ and \aaz\ production.}
+    \end{array}\right.
   \end{split}
 \end{equation}
-and subsequently vary them by the conventional factor 
-of two to estimate higher order contributions.
+Therein, the modified scalar sum of transverse momenta is defined as 
+\begin{equation}
+  \label{ew:defHT}
+  \begin{split}
+    H_\mathrm{T}' = E_\mathrm{T}^V + \sum_{\gamma,q,g} p_{\mathrm{T},i}
+  \end{split}
+\end{equation}
+with $\left.E_\mathrm{T}^W\right.^2=(p_\ell+p_\nu)^2$ and 
+$\left.E_\mathrm{T}^Z\right.^2=(p_{\ell^+}+p_{\ell^-})^2$ 
+in full analogy to the case of the case of vector boson production 
+in association with jets \cite{}.
+As the Born process in each case has no $\muR$ dependence, we 
+do not expect the choice of scale to have a significant influence 
+on the size of the relative QCD and EW corrections.
+We calculate $\mathrm{B}(\muF)$, $\deltaQCD(\muR,\muF)$ and 
+$\deltaEW(\muF^0)$ and vary the free scales $\muR$ and $\muF$ 
+by the conventional factor of two around their central values 
+$\muR^0$ and $\muF^0$, respectively.
+We do not vary the factorisation scale for the determination 
+of $\deltaEW$ as the inherent, albeit normally phenomenologically 
+irrelevant, stabilisation of the $\muF$-dependence at NLO EW 
+is not reflected in our chosen PDF.
+Hence, our NLO EW result exhibits the exact same $\muF$-dependence 
+as the LO result.
 
-We got those results.
-
-We calculate $\mathrm{B}(\muF)$, $\deltaQCD(\muR,\muF)$ and 
-$\deltaEW(\muF^0)$
-
-\begin{table}[h!]
+\begin{table}[t!]
   \centering
@@
 
-\subsection{\texorpdfstring{$\boldsymbol{\gamma\gamma\gamma}$}{aaa} production}
+\subsection[\texorpdfstring{$\gamma\gamma\gamma$}{aaa} production]
+           {$\boldsymbol{\gamma\gamma\gamma}$ production}
 \label{sec:results:aaa}
@@
 
-\subsection{\texorpdfstring{$\boldsymbol{\gamma\gamma\ell\nu}$}{aalnu} production}
+\subsection[\texorpdfstring{$\gamma\gamma\ell\nu$}{aalnu} production]
+           {$\boldsymbol{\gamma\gamma\ell\nu}$ production}
 \label{sec:results:aaw}
@@
 
-\subsection{\texorpdfstring{$\boldsymbol{\gamma\gamma\ell^+\ell^-}$}{aall} production}
+\subsection[\texorpdfstring{$\gamma\gamma\ell^+\ell^-$}{aall} production]
+           {$\boldsymbol{\gamma\gamma\ell^+\ell^-}$ production}
 \label{sec:results:aaz}
@@
 \end{figure}
+
+\begin{figure}[t!]
+  \setlength{\unitlength}{\textwidth}
+  \begin{picture}(0,0.37)
+    \put(0,0.24){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/pT_y1}}
+    \put(0,0.12){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/pT_y2}}
+    \put(0,0){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/pT_l1l2_comb_log}}
+    \put(0.33,0.24){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/m_y1y2_comb_log}}
+    \put(0.33,0.12){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/m_y1l1l2_comb_log}}
+    \put(0.33,0){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/m_y2l1l2_comb_log}}
+    \put(0.66,0.24){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/dphi_y1_y2}}
+    \put(0.66,0.12){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/dphi_y1_l1l2}}
+    \put(0.66,0){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/dphi_y2_l1l2}}
+  \end{picture}
+  \caption{
+    Contribution of $\gamma\gamma$-induced production channels at LO.
+    \label{fig:aaz:aa-ind}
+  }
+\end{figure}

### 2017-10-20 setup.tex
updates to results

@@
 This combination of tools was previously used to calculate the 
-NLO QCD corrections to \ldots \cite{} and the 
-NLO EW corrections to for $\gamma\gamma+0,1,2\,\text{jets}$ production 
+NLO QCD corrections to $ZZ+j$, $h+0,1,2,3\,\text{jets}$ production 
+\cite{Binoth:2009wk,Hoeche:2013mua,Greiner:2015jha,Greiner:2016awe} and the 
+NLO EW corrections to $\gamma\gamma+0,1,2\,\text{jets}$ production 
 in \cite{Chiesa:2017gqx}.
+
+\comment{Shall we cite more or less here?}

### 2017-10-21 results.tex
draft of aaa results section adaption of aaw diagrams to e- production

@@
     $\alphazero$ &\shortequal& $1/137.03599976$  \qquad &&& \\
-    $G_\mu$ &\shortequal& $1.1663787\times 10^{-5}\; \text{GeV}^2$ &&& \\
+    $\Gmu$ &\shortequal& $1.1663787\times 10^{-5}\; \text{GeV}^2$ &&& \\
     $m_W$ &\shortequal& $80.385\; \text{GeV}$       & $\Gamma_W$ &\shortequal& $2.085\; \text{GeV}$ \\
@@
 \end{center}
-Both the width of the top quark and the Higgs boson can safely be 
-neglected as there are no diagrams containing either as $s$-channel 
-propagators which can potentially go on-shell. 
+While we calculate triple photon production in the \alphazero-scheme, 
+we use a mixed scheme for \aaw\ and \aaz production: at LO two 
+powers of $\alpha$ are taken in the \alphazero-scheme, while 
+one power of $\alpha$ is taken in the \Gmu-scheme. 
+The additional power of $\alpha$ in the NLO EW correction 
+is evaluated in \alphazero-scheme again.
+The virtual amplitudes are renormalised correspondingly.
+In all cases both the width of the top quark and the Higgs boson 
+can safely be neglected as there are no diagrams containing either 
+as $s$-channel propagators which can potentially go on-shell. 
 All other lepton and parton masses and widths are set to zero, 
 i.e.\ we are working in the five-flavour scheme.
-We use the \textsc{CT14nlo} PDF set with $\alphas(m_Z)=0.118$. 
+We use the \textsc{CT14nlo} PDF set with $\alphas(m_Z)=0.118$ 
+\cite{}. 
 The use of a QCD-only PDF is justified by the fact that, 
@@
 on the size of the relative QCD and EW corrections.
-We calculate $\mathrm{B}(\muF)$, $\deltaQCD(\muR,\muF)$ and 
-$\deltaEW(\muF^0)$ and vary the free scales $\muR$ and $\muF$ 
+We calculate the leading order cross section $\rd\sigma_\text{LO}(\muF)$, 
+which only depends on the factorisation scale $\muF$, the 
+NLO QCD differential correction factor $\deltaQCD(\muR,\muF)$, 
+introducing the additional $\muR$-dependence, and the NLO EW 
+differential correction factor $\deltaEW(\muF^0)$. 
+To estimate the impact of yet to-be-calculated higher-order 
+corrections we vary the free scales $\muR$ and $\muF$ 
 by the conventional factor of two around their central values 
@@
 as the LO result.
+We define 
+\begin{equation}
+  \label{eq:defnlo}
+  \begin{split}
+    \rd\sigma_\text{NLO QCD}
+    \,=\;&\rd\sigma_\text{LO}\left(1+\deltaQCD\right)\\
+    \rd\sigma_\text{NLO EW}
+    \,=\;&\rd\sigma_\text{LO}\left(1+\deltaEW\right)\\
+    \rd\sigma_\text{NLO \QCDpEW}
+    \,=\;&\rd\sigma_\text{LO}\left(1+\deltaQCD+\deltaEW\right)\\
+    \rd\sigma_\text{NLO \QCDtEW}
+    \,=\;&\rd\sigma_\text{LO}\left(1+\deltaQCD\right)\left(1+\deltaEW\right)\;.
+  \end{split}
+\end{equation}
+Therein, the difference between NLO \QCDpEW\ and NLO \QCDtEW, which 
+is of relative $\order(\alphas\alpha)$, can serve as an indicator 
+of the potential size of unknown corrections at that order.
+
+In Table \ref{tab:xsec} we quote the inclusive cross sections for all 
+three processes. 
+The fiducial cuts for each process is detailed in its 
+respective subsection below. 
+We note that the NLO QCD corrections for both triple photon 
+production and \aaw\ production are strongly jet veto dependent, 
+a result that was previously discussed in great detail in 
+\cite{Bozzi:2011en,Bozzi:2011wwa}, and will be revisited in the 
+following. 
+A much milder jet veto dependence is found for \aaz\ production. 
+The electroweak corrections to inclusive cross sections are 
+generally much smaller, ranging from ..\% (\aaa) to ..\% (\aaw) 
+and ..\% (\aaz).
 
@@
 
+The triple photon production process is defined 
+by the presence of three identified photons in the 
+central detector. 
+To this end we use the smooth cone isolation 
+criterion \cite{Frixione:1998jh}, limiting the amount of 
+hadronic activity in a cone $R_\gamma$ to
+\begin{equation}
+  \begin{split}
+    E_{{\rm had, max}} (r_{\gamma})
+    = \epsilon\, \pT^{\gamma} \left( \frac{1-\cos r_\gamma}
+				       {1-\cos R_\gamma}\right)^{n}\;,
+  \end{split}
+  \label{eq:frix}
+\end{equation}
+where $r_{\gamma}$ denotes the angular separation between the photon and 
+the parton, with 
+\begin{equation}
+  \label{eq:coneparams}
+  \begin{split}
+    R_{\gamma}=0.4\;, \quad \epsilon = 0.05\;, \quad n = 1\;, 
+  \end{split}
+\end{equation}
+to define isolated photon candidates.
+These candidates are then ordered in transverse momentum. 
+We then require at least three such candidates within $|\eta|<2.37$, 
+the leading one of which needs $\pT>40\,\text{GeV}$, 
+while the all subleading ones need only 
+$\pT>30\,\text{GeV}$. 
+Finally, a pairwise separation of $\Delta R(\gamma_i,\gamma_j)>0.4$ 
+between all identified photons is required.
+It is worth noting that at NLO EW it is possible to find more 
+than three isolated photons, in which case any combination may 
+fulfill the above criteria.
+
 \begin{figure}[t!]
@@
 
+Figure \ref{fig:aaa:pt} displays the transverse momenta of the 
+first three leading photons. 
+The NLO QCD corrections exhibit a handful of interesting features. 
+Firstly, in the absence of a jet veto the fixed-order calculation 
+exhibits a huge correction factors, mainly induced by the 
+opening of new channels in the real emission. 
+Similar, kinematic constraints present at LO \footnote{
+  At leading order the leading photon needs to be in a different 
+  hemisphere than both the subleading and third leading photon. 
+  Thus, $\Delta\phi_{\gamma_1\gamma_2}$ and $\Delta\phi_{\gamma_1\gamma_3}$ 
+  must be larger that $\tfrac{1}{2}\,\pi$.
+} are released and 
+lead to a larger phase space that can be populated. 
+These findings mandate the inclusion of at least the $\aaa+\text{jet}$ 
+production process at NLO QCD to arrive at a reliable description 
+of inclusive \aaa\ production, and thus either a NNLO QCD calculation 
+or a multijet merging ansatz \cite{Hoeche:2012yf,Kallweit:2015dum}. 
+While the inclusive QCD corrections at very small transverse momenta 
+are universally large for all three leading photon \pT-spectra 
+($\deltaQCD\approx 2$), they remain at exorbitantly large 
+($\deltaQCD\approx 1.5$) throughout the considered range 
+only for the leading jet \pT. 
+For both subleading photons the QCD corrections are quickly 
+decreasing, leveling out at a $\approx 20\%$ at large transverse 
+momenta.
+In the presence of a restrictive jet veto the very low transverse 
+momentum region still experiences large correction of about 
+$\deltaQCD\approx 1$. 
+As transverse momenta are increasing, the QCD corrections now turn 
+negative reaching now $-50-60\%$ and for all three photons.
+
+The electroweak corrections, due to the absence of the opening 
+of large new channels at the next-to-leading order, are dominated 
+by the virtual corrections. 
+Consequently, the phase space restrictions present at leading 
+order are still respected.
+For all three photons they are small but positive at small 
+transverse momenta and exhibit the usual Sudakov shape at 
+large transverse momenta.
+They reach $-10\%$ for the leading and subleading photon and 
+$-20\%$ for the third photon at $\pT=500\,\text{GeV}$. 
+Due to the different sizes of the QCD and electroweak 
+corrections, the additive and multiplicative combination 
+of corrections lead to very similar results.
+
 \begin{figure}[t!]
@@
     in triple photon production at the LHC at 13\,TeV. 
-    Details as in Fig.\ \ref{fig:aaa:pt}.\\
-    \comment{MS: Spike in $m_{\gamma_1\gamma_2}$ is in NLO \QCDtEW\ 
-             and comes from $\deltaEW\approx 10$ in this bin at the 
-             edge of the LO phase space.}
+    Details as in Fig.\ \ref{fig:aaa:pt}.
     \label{fig:aaa:myy}
@@
 \end{figure}
+
+Figure \ref{fig:aaa:myy} continues with the three diphoton 
+invariant masses. 
+The \pT\ and $\Delta R$ requirements 
+of the event selection induce a minimum in the distributions 
+at leading order. 
+The region below can only be filled if a fourth particle is 
+present, as is the case in both the QCD and electroweak real 
+emission corrections, leading to simultaneously huge 
+corrections \deltaQCD\ and \deltaEW\ as the Born cross 
+section vanishes. 
+Due to this behaviour, the multiplicative combination of 
+corrections, NLO \QCDtEW, ceases to be well defined and 
+spikes in the distribution are visible.
+The distributions below, where $\rd\sigma_\text{LO}=0$, 
+are ill-defined. 
+In consequence, for distributions where kinematic boundaries 
+exist at leading order, but are lifted at higher orders, 
+the multiplicative combination does not present a viable 
+option for a good description of the observable 
+throughout phase space.
+
+The QCD corrections themselves again exceed $200\%$ at 
+small invariant masses, already well before the above 
+described kinematic boundary effect takes hold. 
+As the invariant masses are increasing, the 
+QCD corrections are dropping to $20-30\%$ for the inclusive 
+selection. 
+The structure the QCD corrections exhibit around 80-90\,GeV 
+in all three diphoton-pair invariant masses are induced by 
+the acceptance cuts.
+In the presence of the jet veto, the QCD corrections are 
+reduced and turn negative beyond $m_{\gamma\gamma}\gtrsim 300\,\text{GeV}$ 
+reaching around $-40\%$ at 1\,TeV. 
+The electroweak corrections, on the other hand, are 
+again moderate, ranging from $+1.5\%$ between 70 and 200\,GeV 
+for $m_{\gamma_1\gamma_2}$ and $m_{\gamma_1\gamma_2}$ and 
+0 and 100\,GeV for $m_{\gamma_2\gamma_3}$. 
+$m_{\gamma_1\gamma_2}$ exhibits a small rise in the correction 
+at $2m_W$ due to resonant box diagrams in that region. 
+This feature is also present in the electroweak corrections 
+to diphoton production in this observable \cite{Chiesa:2017gqx}. 
+At large transverse momentum the usual Sudakov logarithms 
+are recoveren, resulting in corrections of around 
+$-8\%$ at 1\,TeV for all photon-pair invariant masses.
 
@@
     in triple photon production at the LHC at 13\,TeV. 
-    Details as in Fig.\ \ref{fig:aaa:pt}.\\
-    \comment{MS: Spike in $\Delta\phi_{\gamma_2\gamma_3}$ is in NLO \QCDtEW\ 
-             and comes from $\deltaEW\approx 2$ in this bin at the 
-             edge of the LO phase space.}
+    Details as in Fig.\ \ref{fig:aaa:pt}.
     \label{fig:aaa:dphi}
@@
 
+Finally, in Figure \ref{fig:aaa:dphi} we show the azimuthal 
+separation $\Delta\phi$ between all three diphoton pairs. 
+Similar features as before are visible as both the NLO QCD 
+and NLO EW corrections relax the kinematic boundaries of 
+the leading order calculation. 
+Especially the azimuthal separation of the leading and 
+third leading photon receives substantial shape corrections 
+throughout the entire spectrum, with and without the 
+presence of a jet veto. 
+The electroweak corrections are negligible for this 
+observable.
+
 \begin{itemize}
   \item \pT of 3rd photon much softer than 1st and 2nd
-  \item EW corrections to \pT of 1st and 2nd photon nearly identical and 
-        $\approx -10\%$ at 500\,GeV, 3rd photon almost twice that.
   \item in all cases NLO EW outside LO uncertainty band
-  \item NLO QCD dominated by real corrections, i.e.\ additional 
-        jet emissions
-  \item intensified through opening of new $qg$ channels and large 
-        gluon luminosity
-  \item can be controlled in fixed-order calculations through jet veto, 
-        needs proper multijet merging
-  \item because at LO the leading jet needs to be in the opposite 
-        hemisphere as the subleading and third leading jet, 
-        $m_{\gamma_1\gamma_2}$ and $m_{\gamma_1\gamma_3}$ 
-        exhibit kinematic edges at LO
-  \item kinematic conditions relaxed at NLO (both QCD and EW, 
-        but QCD dominating), large corrections around those edges, 
-        leads to artifacts in multiplicative combination
-  \item NLO QCD very similar for $m_{\gamma_1\gamma_2}$ and 
-	$m_{\gamma_1\gamma_3}$, $m_{\gamma_2\gamma_3}$ with interesting 
-	structure around 80-90\,GeV
-  \item $m_{\gamma_1\gamma_2}$ again exhibits small excess at $2m_W$
-  \item small positive EW corrections at small $m_{\gamma\gamma}$ 
-  \item $\approx -10\%$ at 1\,TeV for all $m_{\gamma\gamma}$ 
-  \item NLO EW very similar for all $m_{\gamma\gamma}$ 
 \end{itemize}

### 2017-10-25 results.tex
small overhaul of aaa results section

@@
     The distributions are shown at LO (blue), NLO QCD (green), 
-    NLO EW (orange), NLO \QCDpEW\ (red) and NLO \QCDtEW\ (black) 
+    NLO EW (orange), NLO \QCDpEW\ (black) and NLO \QCDtEW\ (red) 
     including scale uncertainties. The top ratio plot details 
@@
 first three leading photons. 
+The first observation is that, with the chosen set of cuts, 
+the leading and subleading photon are of similar hardness, 
+and generally much harder than the third leading photon. 
+This suggest that we select primarily diphoton production events 
+which is accompanied by a third, most bremsstrahlung, photon. 
 The NLO QCD corrections exhibit a handful of interesting features. 
-Firstly, in the absence of a jet veto the fixed-order calculation 
+In the absence of a jet veto the fixed-order calculation 
 exhibits a huge correction factors, mainly induced by the 
@@
 by the virtual corrections. 
-Consequently, the phase space restrictions present at leading 
-order are still respected.
-For all three photons they are small but positive at small 
-transverse momenta and exhibit the usual Sudakov shape at 
-large transverse momenta.
+Consequently, the release of the LO phase space restrictions 
+in the real emission corrections only plays a minor role.
+For all three photons the electroweak corrections are small but 
+positive at small transverse momenta and exhibit the usual 
+Sudakov shape at large transverse momenta.
 They reach $-10\%$ for the leading and subleading photon and 
 $-20\%$ for the third photon at $\pT=500\,\text{GeV}$. 
+More importantly, beyond $\pT\gtrsim 170$, 140 and 80\,GeV 
+for the first, second and third leading photon, respectively, 
+the electroweak corrections are not covered by the LO 
+uncertainty estimate.
 Due to the different sizes of the QCD and electroweak 
@@
 
-Figure \ref{fig:aaa:myy} continues with the three diphoton 
-invariant masses. 
+Figure \ref{fig:aaa:myy} continues with the three combinations of 
+diphoton invariant masses. 
 The \pT\ and $\Delta R$ requirements 
@@
 the multiplicative combination does not present a viable 
-option for a good description of the observable 
+option for describing the observable 
 throughout phase space.
@@
 $-8\%$ at 1\,TeV for all photon-pair invariant masses. 
+Most importantly, beyond $m_{\gamma\gamma}\gtrsim 300\,\text{GeV}$, 
+the electroweak corrections are again not covered by the LO 
+uncertainty estimate.
 
@@
 
-\begin{itemize}
-  \item \pT of 3rd photon much softer than 1st and 2nd
-  \item in all cases NLO EW outside LO uncertainty band
-\end{itemize}
-
 \subsection[\texorpdfstring{$\gamma\gamma\ell\nu$}{aalnu} production]
@@
 
-\comment{MS: is that $\ell^+$ or $\ell^-$?}
+Next we move on
 

### 2017-10-25 results.tex
draft of aaw section

@@
 
-Next we move on
+Next we move on to diphoton production in association with 
+a $W$ boson decaying leptonically.
+In this context, we will representatively focus on $W^-$ bosons 
+as we do not expect qualitatively different results for $W^+$ 
+bosons. 
+We define our fiducial phase space by the following. 
+First, we require the presence of exactly one charged lepton, 
+dressed with all photons in a cone of size $R=0.1$, with 
+$\pT>20\,\text{GeV}$ and $|\eta|<2.47$. 
+Among the remaining photons we require at least two identified 
+ones, using the procedure described in Sec.\ \ref{sec:results:aaa}, 
+only changing the transverse momentum requirements to 
+$\pT>20\,\text{GeV}$ for both the leading and the subleading 
+identified photon. 
+We further demand the angular separation of both photons 
+to be $\Delta R(\gamma_1,\gamma_2)>0.4$ and each photon and 
+the lepton to be $\Delta R(\ell,\gamma)>0.4$.
+We put no requirements on the missing transverse momentum. 
+The inclusive cross sections and correction factors were 
+detailed in Tab.\ \ref{tab:xsec}.
+\comment{MS: Nico, please check!}
 
@@
 
+Figure \ref{fig:aaw:pt} shows the transverse momenta of 
+the leading and subleading photon as well as the charged 
+lepton. 
+As was observed in tiple photon production, the inclusive 
+NLO QCD corrections are large. 
+Nonetheless, they differ substatially between the three 
+oberservables and in their different regions. 
+While $\deltaQCD$ rises from values of 0.3 at small 
+transverse momenta of the leading photon to 2 at 
+$\pT\approx 100\,\text{GeV}$, it remains constant above that 
+value.
+In the subleading photon's transverse momentum, the 
+situation is different. 
+Experiencing a cut-induced jump from 0.3 to 2.5 at low \pT, 
+it decreases steadily thereafter to reach $\deltaQCD=0.8$ 
+at 500\,GeV. 
+The behaviour of the QCD corrections to the lepton \pT are 
+then again qualitatively similar to that of the leading 
+photon, start at $\deltaQCD=0.8$ at low \pT and rising 
+steeply to 2.5 at 100\,GeV and then gradually leveling out 
+at 3.5. 
+Again, the presence of a restrictive jet veto has little 
+effect on the small transverse momentum regions, but 
+effectively contains the size of the NLO QCD corrections 
+to remain below $\deltaQCD=0.5$. 
+Instead, they are again driven negative, reaching 
+$-20-30\%$ for all three observables.
+
+The electroweak corrections are negative throughout, 
+reaching $-20\%$ for the leading photon and the lepton 
+and $-20\%$ for the subleading photon at 500\,GeV. 
+For this process, starting at transverse momenta of 
+around 100\,GeV, the electroweak corrections are much 
+larger than the LO uncertainty estimate.
+Due to their larger size, as compared with the \aaa\ 
+production process, the difference between their 
+additive and multiplicative combination with the 
+QCD corrections becomes more pronounced when no 
+jet veto is applied. 
+One reason is that the QCD corrections are dominated 
+by real emission contributions, which only receive the 
+not-so-small electroweak correction factor in the 
+multiplicative combination, but not the additive one. 
+While this correction factor is, strictly speaking, 
+associated only with the Born configuration, its 
+application to real-emission configurations is well 
+motivated in the electroweak Sudakov-regime at 
+large transverse momenta. 
+The concurrence of the additive and multiplicative 
+schemes in the presence of the jet veto now precisely 
+originates in the taming of the QCD corrections by 
+restricting the influence of real-emission topologies.
+
 \begin{figure}[t!]
@@
     leading and third leading photon (centre), subleading and third leading 
-    photon (right) at the LHC at 13\,TeV.\\
-    \comment{MS: Spike in $m_{\gamma_1\gamma_2}$ is in NLO \QCDtEW 
-             and comes from $\deltaEW\approx 10$ in this bin at the 
-             edge of the LO phase space.}
+    photon (right) at the LHC at 13\,TeV.
     \label{fig:aaw:myy}
@@
 \end{figure}
+
+Considering now the invariant mass of both photons 
+and the leading photon and the lepton, presented in 
+Figure \ref{fig:aaw:myy}, a similar picture 
+presents itself. 
+Both QCD corrections are moderate at small invariant 
+masses and increase as the invariant mass rises. 
+While $m_{\gamma_1\gamma_2}$ developes a correction 
+factor of $\deltaQCD=2$ at 200\,GeV and then falls 
+again to 0.4 at 1\,TeV, $m_{\gamma_1\ell}$ only 
+reaches a maximum of $\deltaQCD=1.3$ before falling 
+to 0.4 as well. 
+In the presence of a jet veto, the shape of the corrections 
+remains similar, but their magnitude is contained to 
+be smaller than 0.5, turning negative around 500\,GeV 
+for both observables. 
+The electroweak corrections are again negative 
+throughout, reaching $-15-20\%$ at invariant masses 
+of 1\,TeV.
+Again, above 200\,GeV they are consistently outside 
+the LO uncertainty estimate and play an important 
+role.
+
+Figure \ref{fig:aaa:myy} also displays the transverse 
+mass of the $W$ boson on the right hand side. 
+This distribution exhibits the general features known 
+from inclusive $W$ production, only the QCD corrections 
+are scaled to the values present in this process.
+Electroweak corrections are less pronounced than for 
+the invariant masses, but are still non-negligible. 
+They reach about $-8\%$ at $m_\text{T}=200\,\text{GeV}$ 
+and $-14\%$ at 1\,TeV.
 
@@
     leading and third leading photon (centre), subleading and third leading 
-    photon (right) at the LHC at 13\,TeV.\\
-    \comment{MS: Spike in $m_{\gamma_1\gamma_2}$ is in NLO \QCDtEW 
-             and comes from $\deltaEW\approx 10$ in this bin at the 
-             edge of the LO phase space.}
+    photon (right) at the LHC at 13\,TeV.
     \label{fig:aaw:dphi}
@@
 
+Finally, Figure \ref{fig:aaw:dphi} presents the azimuthal 
+separations of the leading and the subleading photon, and 
+both the leading and subleading photon and the lepton. 
+Contrary to \aaa\ production, no kinematic constraints 
+are present at LO, owing to the difference in flavour 
+between the considered objects and the fact that the 
+lepton is only one of two decay products of the $W$ which 
+takes the role of the third photon from point of view of 
+the contributing diagrams.
+
+Both the QCD and EW corrections are generally flat, taking 
+values of typically $\deltaQCD=1-2$ in absence and 
+$\deltaQCD=0.4$ in presence of a jet veto, and 
+$\deltaEW=-2\%$.
+
+As none of the observables considered for this process 
+exhibits a kinematic boundary at LO that is lifted at 
+NLO, both the additive and the multiplicative combination 
+of QCD and EW corrections present a viable prediction 
+throughout and their difference can be taken as an 
+indication of the potential size of higher-order corrections 
+of $\order(\alphas\alpha)$.
+
 \subsection[\texorpdfstring{$\gamma\gamma\ell^+\ell^-$}{aall} production]
@@
 \label{sec:results:aaz}
+
+Finally, we consider diphoton production in association with 
+a $Z$ boson in its leptonic decay channel. 
+In practise we look at lepton pair production including 
+all non-resonant diagrams.
+The fiducial phase space of our analysis is defined as follows. 
+First, we require the presence of exactly one lepton pair 
+of opposite charge, dressed with all photons in a cone of 
+size $R=0.1$, with $\pT>20\,\text{GeV}$ and $|\eta|<2.47$. 
+Their invariant mass must be larger than 40\,GeV. 
+As in the case of \aaw production, we then require at least 
+two identified photons among the remaining ones after dressing, 
+using the procedure described in Sec.\ \ref{sec:results:aaa}, 
+again loosening the transverse momentum requirements to 
+$\pT>20\,\text{GeV}$ for both the leading and the subleading 
+identified photon. 
+We further demand the angular separation of both photons 
+to be $\Delta R(\gamma_1,\gamma_2)>0.4$ and each photon and 
+the lepton to be $\Delta R(\ell,\gamma)>0.4$.
+We put no requirements on the missing transverse momentum. 
+The inclusive cross sections and correction factors were 
+detailed in Tab.\ \ref{tab:xsec}.
+\comment{MS: Nico, please check!}
 
@@
     at the LHC at 13\,TeV. 
-    Details as in Fig.\ \ref{fig:aaa:pt}.\\
-    \comment{MS: Spike in $m_{\gamma_1\ell_1\ell_2}$ is in NLO \QCDtEW\ 
-             and comes from $\deltaEW\approx 10$ in this bin at the 
-             edge of the LO phase space.}
+    Details as in Fig.\ \ref{fig:aaa:pt}.
     \label{fig:aaz:myy}
@@
     at the LHC at 13\,TeV. 
-    Details as in Fig.\ \ref{fig:aaa:pt}.\\
-    \comment{MS: Spike in $\Delta\phi_{\gamma_1,\ell_1\ell_2}$ is in NLO \QCDtEW\ 
-             and comes from $\deltaEW\approx 10$ in this bin at the 
-             edge of the LO phase space.}
+    Details as in Fig.\ \ref{fig:aaa:pt}.
     \label{fig:aaz:dphi}

### 2017-10-25 results.tex
draft of aaz part

@@
 
+In close analogy with the previous two processes considered, 
+we start our discussion of the results with the transverse 
+momenta of the leading and subleading photon and the charged 
+lepton pair, cf.\ Figure \ref{fig:aaz:pt}. 
+The first observation is, while the general behaviour of the 
+spectra is the same as in \aaw production, the inclusive QCD 
+corrections are much smaller in this case. 
+They range between $\deltaQCD=0.3-0.4$ for the leading and 
+subleading photon and rise to 0.7 for the lepton pair at 
+500\,GeV. 
+The restrictive jet veto employed for the previous process 
+reduces the QCD corrections further. 
+Beyond the negligible impact at very small transverse 
+momenta, they turn negative early on, reaching $\deltaQCD=-0.2-0.4$ 
+at 500\,GeV. 
+The electroweak corrections negative throughout, increasing 
+from $\deltaEW=-5\%$ at low transverse momenta to $-20\%$ at 
+500\,GeV.
+They are consistently larger than the LO uncertainty estimate. 
+As a consequence, the difference between the additive and 
+multiplicative is comparably large, especially in the high 
+\pT regions.
+
 \begin{figure}[t!]
@@
 
+Figure \ref{fig:aaz:myy} continues to display the invariant masses 
+of the leading and subleading photon, and both the leading and 
+subleading photon and the lepton pair. 
+The familiar peak in $m_{\gamma_i\ell^+\ell^-}$ is produced by 
+configurations where the respective photon is emitted by the 
+lepton-pair from a resonant $Z$ boson decay. 
+Again, the QCD corrections are moderate, always staying below 
+$\deltaQCD=0.4$ and of a similar shape as encoutered already in 
+\aaw\ production. 
+The jet veto again reduces the QCD correction and drives in negative 
+in large portions of the observable range, reaching as much as 
+$\deltaQCD=-0.5$ for the diphoton invariant mass. 
+The electroweak corrections, on the other hand, are very similar 
+to the \aaw case: with the exception of the well known positive 
+radiative corrections below the $Z$ peak, they are negative 
+throughout, reaching $\deltaEW=-20\%$ at invariant masses of 
+1\,TeV.
+As in the case of the transverse momenta, due to the similar size 
+of the QCD and electroweak corrections at large transverse 
+momenta, the difference between their additive and the multiplicative 
+combination is amplified.
+
 \begin{figure}[t!]
@@
 \end{figure}
+
+In Figure \ref{fig:aaz:dphi} we consider the azimuthal separation 
+between the leading and subleading photon, and both the leading 
+and subleading photon and the lepton pair.
+While the both photons tend to be back-to-back, the azimuthal 
+separation of the leading photon and the lepton pair exhibits 
+a kinematic edge at LO, restricting it to be larger than 
+$\tfrac{1}{2}\,\pi$. 
+\comment{MS: Do we understand why this is?}
+On the contrary, the azimuthal separation of the subleading 
+photon and the lepton pair exhibits no such limit at LO and 
+instead peaks at roughly $\Delta\phi=\tfrac{1}{2}\,\pi$. 
+The QCD corrections, with the exception of the aforementioned 
+edge, are generally flat, taking values of $\deltaQCD\approx 0.3$ 
+in the absence and $\deltaQCD\approx 0.2$ in the presence 
+of a jet veto. 
+The electroweak corrections are equally flat and amount to 
+$\deltaEW\approx-4\%$. 
+Their additive and multiplicative combinations are very 
+similar.
 
@@
 \end{figure}
+
+Finally, \aaz\ production is the only process of the three processes 
+considered in this publication which can be produced through 
+photon-induced channels at leading order, 
+$\gamma\gamma\to\ell^+\ell^-\gamma\gamma$. 
+To this end, we investigate their contribution at LO in 
+Figure \ref{fig:aaz:aa-ind}. 
+The photon-induced contribution is typically a few per mille of the 
+LO cross section, but raises up to 2\% for invariant masses larger 
+than 1\,TeV, especially $m_{\gamma_i\ell^+\ell^-}$. 
+In this region, however, typical QCD and EW corrections are much larger 
+such that this contribution can be safely ignored. 
+As the photon-induced processes only contribute through non-resonant 
+lepton-pair production, their contribution can be further suppressed 
+by tightening the acceptance window in the lepton-pair invariant mass.

### 2017-10-25 results.tex
update xs table

@@
 The electroweak corrections to inclusive cross sections are 
-generally much smaller, ranging from ..\% (\aaa) to ..\% (\aaw) 
-and ..\% (\aaz).
+generally much smaller, ranging from $0.6\%$ (\aaa) to $-1.8\%$ (\aaw) 
+and $-4.6\%$ (\aaz).
 
 \begin{table}[t!]
-  \centering
-  \begin{tabular}{l||c|c|c}
-      & $\;\;pp \to \gamma \gamma\gamma\;\;$
-      & $\;\;pp \to \gamma \gamma e^-\bar\nu_e\;\;$ 
-      & $\;\;pp \to \gamma \gamma e^+e^-\;\;$ \\
-    \hline\hline
-    $\sigma_\text{LO}\;\;[\text{pb}] $ &  &  & \\
-    \hline
-    $\delta_\text{QCD}\;\;[\text{pb}]\;\;\pTveto=\infty $ &  &  & \\
-    \hline
-    $\delta_\text{QCD}\;\;[\text{pb}]\;\;\pTveto=30\,\text{GeV} $ &  &  & \\
-    \hline
-    $\delta_\text{EW}\;\;[\text{pb}] $ &  &  & \\
-  \end{tabular}
+  \input{xs}
   \caption{
@@
     \put(0,0.24){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/pT_y1}}
-    \put(0,0.12){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/pT_y2}}
-    \put(0,0){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/pT_l1l2_comb_log}}
-    \put(0.33,0.24){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/m_y1y2_comb_log}}
+    \put(0,0.12){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/m_y1y2_comb_log}}
+    \put(0,0){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/dphi_y1_y2}}
+    \put(0.33,0.24){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/pT_y2}}
     \put(0.33,0.12){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/m_y1l1l2_comb_log}}
-    \put(0.33,0){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/m_y2l1l2_comb_log}}
-    \put(0.66,0.24){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/dphi_y1_y2}}
-    \put(0.66,0.12){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/dphi_y1_l1l2}}
+    \put(0.33,0){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/dphi_y1_l1l2}}
+    \put(0.66,0.24){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/pT_l1l2_comb_log}}
+    \put(0.66,0.12){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/m_y2l1l2_comb_log}}
     \put(0.66,0){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/dphi_y2_l1l2}}

### 2017-10-29 aaV_main.tex
few mods
updates
updates to results
draft of aaa results section adaption of aaw diagrams to e- production
update xs table
update draft, added abstract and conclusions

@@
 \pdfoutput=1
-\setlength\parindent{0pt}
+% \setlength\parindent{0pt}
 
@@
 
+\newlength{\unitcharwidth}
+\settowidth{\unitcharwidth}{1}
+
+\newlength{\unitsuperscriptwidth}
+\settowidth{\unitsuperscriptwidth}{\scriptsize 1}
+
 %%% Macros
+\newcommand{\rd}{\ensuremath{\mathrm{d}}}
 \newcommand{\eqn}[1]{Eq.~(\ref{#1})}
-\newcommand{\ab}{\ensuremath{\alpha_0}}
-\newcommand{\als}{\ensuremath{\alpha_s}}
-\newcommand{\aapa}{\ensuremath{\gamma\gamma}}
+\newcommand{\Gmu}{\ensuremath{G_\mu}}
+\newcommand{\alphazero}{\ensuremath{\alpha(0)}}
+\newcommand{\alphaGmu}{\ensuremath{\alpha_{\Gmu}}}
+\newcommand{\alphas}{\ensuremath{\alpha_s}}
+\newcommand{\aaa}{\ensuremath{\gamma\gamma\gamma}}
+\newcommand{\aaw}{\ensuremath{\gamma\gamma W}}
+\newcommand{\aaz}{\ensuremath{\gamma\gamma Z}}
 \newcommand{\shortequal}{\ensuremath{\!\!\!=\!\!\!}}
 \newcommand{\pT}{\ensuremath{p_\text{T}}}
+\newcommand{\pTveto}{\ensuremath{p_\text{T,jet}^\text{veto}}}
 \newcommand{\order}{\ensuremath{\mathcal{O}}}
+\newcommand{\vP}{\ensuremath{\vphantom{\int_a^b}}}
 
@@
 \newcommand{\RESBOS}{R\scalebox{0.8}{ESBOS}\xspace}
+
+\newcommand{\QCDpEW}{QCD+EW}
+\newcommand{\QCDtEW}{QCD$\times$EW}
+\newcommand{\deltaQCD}{\ensuremath{\delta_\text{QCD}}}
+\newcommand{\deltaEW}{\ensuremath{\delta_\text{EW}}}
+\newcommand{\muR}{\ensuremath{\mu_{\mathrm{R}}}}
+\newcommand{\muF}{\ensuremath{\mu_{\mathrm{F}}}}
 
@@
 \abstract{
-  We calculate the next-to-leading order electroweak corrections...
+Processes with three external electroweak gauge boson allow for a measurement of triple and quartic gauge
+couplings. They allow for a constraint of anomalous gauge couplings, where new physics might predominantly
+couple to electroweak gauge bosons. In this paper we chose a class of such processes where we consider two photons
+and an additional vector boson in the final state. As additional vector boson we consider either a third photon or a
+$W$ or $Z$ boson. For the latter two cases we assume a leptonic decay of the boson. We calculate the next-to-leading
+order QCD and electroweak corrections to these processes with a particular emphasize on the until now unknown 
+electroweak corrections. We find that the electroweak corrections to the total cross section are moderate in the range of a few 
+per cent at most, but can reach several tens of per cent in regions of phase space  that are particularly interesting
+ in the context of new physics searches. In addition we investigate the difference between additive and multiplicative scheme 
+ when combining
+QCD and electroweak corrections and we asess the importance of photon induced contributions to these processes. 
 }

### 2017-10-29 conclusions.tex
update draft, added abstract and conclusions

@@
 \label{sec:conclusions}
-
-We did good.
+Processes that involve vertices of three and four electroweak gauge bosons are among the most promising processes
+where new physics might be found. Deviations from the Standard Model couplings or vertices that do not exist in the 
+Standard Model might be found. The deviations from the Standard Model predictions can for instance conveniently 
+described by higher dimensional operators in terms of an effective field theory. Precise measurements of these  
+processes allow to constrain and set limits to these higher dimensional operators.\\
+In this paper we investigated the Standard Model predictions to a subset of such processes where we require
+two photons plus an additional electroweak vector boson in the final state.  As additional vector boson we allowed
+for a third photon a well as for a $W$ or $Z$ boson where we considered the leptonic decay of the heavy bosons.
+This particularly implies that all non-resonant contributions are taken into account as well.\\
+We calculated the next-to-leading order QCD and electroweak corrections to these three processes for a set
+of fiducial cuts. Particular
+emphasize has been put on the up to now unknown electroweak corrections as well as the combination of QCD and
+electroweak corrections with the aim of producing the most precise prediction possible within the Standard Model.
+As expected we found the QCD corrections to be large and dominant compared to the electroweak corrections when 
+calculating the corrections to the total cross sections. QCD corrections are particular large for these processes due to new
+channels opening up at NLO but can effectively be reduced by applying a jet veto. Electroweak corrections
+lead to moderate corrections to the total cross section of up to a few per cent for the $\gamma\gamma l^{+}l^{-}$ 
+process. However, in the high energy tail of differential distributions the electroweak corrections become increasingly important
+and can lead to corrections of up to $30 \%$. Electroweak corrections become important in the same regions where one
+also expects increasing effects of higher dimensional operators. The precise determination of limits on higher dimensional 
+operators therefore requires the inclusion of higher order correction of both QCD as well as of the electroweak interaction.

### 2017-10-29 results.tex
implement alpha(0) for NLO EW
update draft, added abstract and conclusions

@@
 We use the \textsc{CT14nlo} PDF set with $\alphas(m_Z)=0.118$ 
-\cite{}. 
+\cite{Dulat:2015mca}, interfaced through LHAPDF6 \cite{Buckley:2014ana}. 
 The use of a QCD-only PDF is justified by the fact that, 
@@
   \label{eq:murfdef}
-  \begin{split}
-    \muR^0 = \muF^0 = \left\{
-    \begin{array}{ll}
-      m_{\aaa} \qquad & \text{in \aaa\ production} \\[2mm]
-      \tfrac{1}{2}\,H_T' & \text{in \aaw\ and \aaz\ production.}
-    \end{array}\right.
-  \end{split}
+  %\begin{split}
+    \muR^0 = \muF^0 = %\left\{
+    %\begin{array}{ll}
+     % m_{\aaa} \qquad & \text{in \aaa\ production} \\[2mm]
+      \tfrac{1}{2}\,H_T' \;. %& \text{in \aaw\ and \aaz\ production.}
+    %\end{array}\right.
+  %\end{split}
 \end{equation}
-Therein, the modified scalar sum of transverse momenta is defined as 
+In the case of the triple photon process $ H_\mathrm{T}' $ is just given by the scalar sum of all final state 
+transverse momenta, for the two processes with the massive vector bosons it is defined as 
 \begin{equation}
@@
 in full analogy to the case of the case of vector boson production 
-in association with jets \cite{}.
+in association with jets \cite{Berger:2009ep}.
 As the Born process in each case has no $\muR$ dependence, we 
@@
 generally much smaller, ranging from $0.6\%$ (\aaa) to $-1.8\%$ (\aaw) 
-and $-4.6\%$ (\aaz).
+and $-4.4\%$ (\aaz).
 
@@
 At large transverse momentum the usual Sudakov logarithms 
-are recoveren, resulting in corrections of around 
+are recovered, resulting in corrections of around 
 $-8\%$ at 1\,TeV for all photon-pair invariant masses. 
@@
 dressed with all photons in a cone of size $R=0.1$, with 
-$\pT>20\,\text{GeV}$ and $|\eta|<2.47$. 
+$\pT>20\,\text{GeV}$ and $|\eta|<2.5$. 
 Among the remaining photons we require at least two identified 
@@
 to be $\Delta R(\gamma_1,\gamma_2)>0.4$ and each photon and 
-the lepton to be $\Delta R(\ell,\gamma)>0.4$.
-We put no requirements on the missing transverse momentum. 
+the lepton to be $\Delta R(\ell,\gamma)>0.7$.
+Furthermore we require the transverse mass of the lepton-neutrino system
+to be larger than $40\, \text{GeV}$.
 The inclusive cross sections and correction factors were 
 detailed in Tab.\ \ref{tab:xsec}.
-\comment{MS: Nico, please check!}
 
@@
 lepton. 
-As was observed in tiple photon production, the inclusive 
+As was observed in triple photon production, the inclusive 
 NLO QCD corrections are large. 
@@
 then again qualitatively similar to that of the leading 
-photon, start at $\deltaQCD=0.8$ at low \pT and rising 
+photon, start at $\deltaQCD=0.8$ at low \pT \, and rising 
 steeply to 2.5 at 100\,GeV and then gradually leveling out 
@@
 reaching $-20\%$ for the leading photon and the lepton 
-and $-20\%$ for the subleading photon at 500\,GeV. 
+and $-25\%$ for the subleading photon at 500\,GeV. 
 For this process, starting at transverse momenta of 
@@
 
-Figure \ref{fig:aaa:myy} also displays the transverse 
+Figure \ref{fig:aaw:myy} also displays the transverse 
 mass of the $W$ boson on the right hand side. 
@@
 using the procedure described in Sec.\ \ref{sec:results:aaa}, 
-again loosening the transverse momentum requirements to 
-$\pT>20\,\text{GeV}$ for both the leading and the subleading 
+loosening the transverse momentum requirements to 
+$\pT>15\,\text{GeV}$ for both the leading and the subleading 
 identified photon. 
@@
 the lepton to be $\Delta R(\ell,\gamma)>0.4$.
-We put no requirements on the missing transverse momentum. 
 The inclusive cross sections and correction factors were 
 detailed in Tab.\ \ref{tab:xsec}.
-\comment{MS: Nico, please check!}
 
@@
 at 500\,GeV. 
-The electroweak corrections negative throughout, increasing 
-from $\deltaEW=-5\%$ at low transverse momenta to $-20\%$ at 
+The electroweak corrections are negative throughout, increasing 
+from $\deltaEW=-4\%$ at low transverse momenta to $-20\%$ at 
 500\,GeV.
@@
 multiplicative is comparably large, especially in the high 
-\pT regions.
+\pT\ regions.
 

### 2017-10-29 setup.tex
update draft, added abstract and conclusions

--- 2017-10-19 setup.tex
@@
 This combination of tools was previously used to calculate the 
-NLO QCD corrections to \ldots \cite{} and the 
-NLO EW corrections to for $\gamma\gamma+0,1,2\,\text{jets}$ production 
+NLO QCD corrections to $ZZ+j$, $h+0,1,2,3\,\text{jets}$ , $W^{+}W^{-}b\bar{b}$ production 
+\cite{Binoth:2009wk,Hoeche:2013mua,Greiner:2015jha,Greiner:2016awe,Heinrich:2013qaa,Heinrich:2017bqp} and the 
+NLO EW corrections to $\gamma\gamma+0,1,2\,\text{jets}$ production 
 in \cite{Chiesa:2017gqx}.

### 2017-10-30 conclusions.tex
updated aaa figs with correct scale denomination, small fixes to setups, results and conclusions

--- 2017-10-03 conclusions.tex
@@
 \label{sec:conclusions}
+Processes that involve vertices of three and four electroweak gauge bosons are among the most promising processes
+where new physics might be found. Deviations from the Standard Model couplings or vertices that do not exist in the 
+Standard Model might be found. The deviations from the Standard Model predictions can for instance conveniently be 
+described by higher dimensional operators in terms of an effective field theory. Precise measurements of these  
+processes allow to constrain and set limits to these higher dimensional operators.
 
-We did good.
+In this paper we investigated the Standard Model predictions to a subset of such processes where we require
+two photons plus an additional electroweak vector boson in the final state.  As additional vector boson we allowed
+for a third photon as well as for a $W$ or $Z$ boson where we considered their leptonic decay modes.
+This particularly implies that all off-shell and non-resonant contributions are taken into account.
+
+We calculated the next-to-leading order QCD and electroweak corrections to these three processes for a set
+of realistic fiducial cuts. Particular
+emphasis has been put on the up to now unknown electroweak corrections as well as the combination of QCD and
+electroweak corrections with the aim of producing the most precise prediction possible within the Standard Model.
+As expected, we found the QCD corrections to be large and dominant compared to the electroweak corrections when 
+calculating the corrections to the total cross sections. QCD corrections are particular large for these processes due to new
+channels opening up at NLO but can effectively be reduced by applying a jet veto. Electroweak corrections
+lead to moderate corrections to the total cross section of up to $4.4\%$ for the $\gamma\gamma \ell^{+}\ell^{-}$ 
+process. However, in the high energy tail of differential distributions the electroweak corrections become increasingly important
+and can lead to corrections of up to $30 \%$. Electroweak corrections become important in the same regions where one
+also expects increasing effects of higher dimensional operators. The precise determination of limits on higher dimensional 
+operators therefore requires the inclusion of higher order correction of both QCD as well as of the electroweak interaction.

### 2017-10-30 results.tex
updated aaa figs with correct scale denomination, small fixes to setups, results and conclusions

@@
 differential correction factor $\deltaEW(\muF^0)$. 
-To estimate the impact of yet to-be-calculated higher-order 
+To estimate the impact of yet-to-be-calculated higher-order 
 corrections we vary the free scales $\muR$ and $\muF$ 
@@
 three processes. 
-The fiducial cuts for each process is detailed in its 
+The set of fiducial cuts for each process is detailed in its 
 respective subsection below. 

### 2017-10-30 setup.tex
updated aaa figs with correct scale denomination, small fixes to setups, results and conclusions

--- 2017-10-19 setup.tex
@@
 This combination of tools was previously used to calculate the 
-NLO QCD corrections to \ldots \cite{} and the 
-NLO EW corrections to for $\gamma\gamma+0,1,2\,\text{jets}$ production 
+NLO QCD corrections to $ZZ+\text{jet}$, $t\bar{t}+0,1\,\text{jets}$, 
+$W^{+}W^{-}b\bar{b}$ and $h+0,1,2,3\,\text{jets}$ production 
+in \cite{Binoth:2009wk,Hoeche:2013mua,Heinrich:2013qaa,
+  Greiner:2015jha,Greiner:2016awe,Heinrich:2017bqp} and the 
+NLO EW corrections to $\gamma\gamma+0,1,2\,\text{jets}$ production 
 in \cite{Chiesa:2017gqx}.

### 2017-10-30 results.tex
minor corrections to results

@@
 These candidates are then ordered in transverse momentum. 
-We then require at least three such candidates within $|\eta|<2.37$, 
+We require at least three such candidates within $|\eta|<2.37$, 
 the leading one of which needs $\pT>40\,\text{GeV}$, 
@@
 This suggest that we select primarily diphoton production events 
-which is accompanied by a third, most bremsstrahlung, photon. 
+which is accompanied by a third, mostly bremsstrahlung, photon. 
 The NLO QCD corrections exhibit a handful of interesting features. 
 In the absence of a jet veto the fixed-order calculation 
-exhibits a huge correction factors, mainly induced by the 
+exhibits huge correction factors, mainly induced by the 
 opening of new channels in the real emission. 
-Similar, kinematic constraints present at LO \footnote{
+Additionally, kinematic constraints present at LO \footnote{
   At leading order the leading photon needs to be in a different 
@@
 For both subleading photons the QCD corrections are quickly 
-decreasing, leveling out at a $\approx 20\%$ at large transverse 
+decreasing, leveling out at a approximately $20\%$ at large transverse 
 momenta.
@@
 $\deltaQCD\approx 1$. 
-As transverse momenta are increasing, the QCD corrections now turn 
+As transverse momenta are increasing, however, the QCD corrections now turn 
 negative reaching now $-50-60\%$ and for all three photons.
@@
 again moderate, ranging from $+1.5\%$ between 70 and 200\,GeV 
-for $m_{\gamma_1\gamma_2}$ and $m_{\gamma_1\gamma_2}$ and 
+for $m_{\gamma_1\gamma_2}$ and $m_{\gamma_1\gamma_3}$ and 
 0 and 100\,GeV for $m_{\gamma_2\gamma_3}$. 
@@
 NLO QCD corrections are large. 
-Nonetheless, they differ substatially between the three 
+Nonetheless, they differ substantially between the three 
 oberservables and in their different regions. 
@@
 situation is different. 
-Experiencing a cut-induced jump from 0.3 to 2.5 at low \pT, 
+Experiencing an acceptance cut induced jump from 0.3 to 2.5 at low \pT, 
 it decreases steadily thereafter to reach $\deltaQCD=0.8$ 
 at 500\,GeV. 
-The behaviour of the QCD corrections to the lepton \pT are 
+The behaviour of the QCD corrections to the lepton \pT\ are 
 then again qualitatively similar to that of the leading 
-photon, start at $\deltaQCD=0.8$ at low \pT \, and rising 
+photon, starting at $\deltaQCD=0.8$ at low \pT \, and rising 
 steeply to 2.5 at 100\,GeV and then gradually leveling out 
@@
 \aaw\ production. 
-The jet veto again reduces the QCD correction and drives in negative 
+The jet veto again reduces the QCD corrections and drives them negative 
 in large portions of the observable range, reaching as much as 
 $\deltaQCD=-0.5$ for the diphoton invariant mass. 
-The electroweak corrections, on the other hand, are very similar 
+The electroweak corrections, on the other hand, are qualitatively very similar 
 to the \aaw case: with the exception of the well known positive 
@@
 and subleading photon and the lepton pair.
-While the both photons tend to be back-to-back, the azimuthal 
+While both photons tend to be back-to-back, the azimuthal 
 separation of the leading photon and the lepton pair exhibits 

### 2017-10-30 conclusions.tex
minor updates in text

@@
 operators therefore requires the inclusion of higher order correction of both QCD as well as of the electroweak interaction.
+We also compared the two possibilities of combining QCD with electroweak corrections, namely either in an additive or
+in a multiplicative way. One expects that the difference between the two schemes is small as they can be seen as an estimation
+of neglected higher order contributions. We found that although this is true on the level of total cross sections there can be 
+regions in phase space where the leading order contribution vanishes and therefore the k-factor become infinitely large. 
+For those kinematical edges we observe a breakdown of the multiplicative scheme whereas the additive scheme provides
+a reliable estimation of the higher order uncertainties throughout the whole phase space.

### 2017-10-30 results.tex
minor updates in text

@@
 throughout the entire spectrum, with and without the 
-presence of a jet veto. 
+presence of a jet veto. The angular distribution between leading photon
+and the second or third subleading photon exhibit a kinematical edge at $\pi/2$ which 
+is relaxed at NLO. 
+This kinematical edge can be understood in the following way:
+ Let us consider the first observable, the angular separation between 
+the leading and the subleading photon, the argument also holds for the separation between
+the leading and the third leading photon. The third leading photon has to recoil against the
+system of the two leading photons. Let us go into the limit where the three photons have
+a very similar transverse momentum and consider the configuration where the leading
+photon is back-to-back to the third leading photon. Then the second photon must 
+be perpendicular to this axis. If the third photon has less transverse momentum, it 
+needs the second photon to recoil against the leading photon. Therefore it gets closer
+to the third photon and further away from the leading photon. $\pi/2$ is therefore the
+minimal distance the second photon can have to the leading one.  Only at NLO where
+one can have additional radiation this constraint is relaxed. We will see later in Fig.
+\ref{fig:aaz:dphi} that this situation is also present when one replaces one of the subleading
+photons by a $z$ boson. 
 The electroweak corrections are negligible for this 
@@
 $\tfrac{1}{2}\,\pi$. 
-\comment{MS: Do we understand why this is?}
+As discussed above this kinematic edge is also present in the case of the triple photon process
+(see Fig. \ref{fig:aaa:dphi_}) when considering the azimuthal angle between
+the leading and any subleading photon.
 On the contrary, the azimuthal separation of the subleading 

### 2017-10-30 aaV_main.tex
cern preprint number
minor updates in text

@@
 \affiliation[a]{Physik Institut, Universit{\"a}t Z{\"u}rich, Winterthurerstr.190, 8057 Z\"urich, Switzerland}
-\affiliation[b]{CERN}
+\affiliation[b]{Theoretical Physics Department, CERN, 1211 Geneva 23, Switzerland}
 
@@
   \begin{flushright}
-    ZU--TH--??, CERN-- 
+    ZU--TH--??\\ CERN-TH-2017-226
   \end{flushright}
@@
 Processes with three external electroweak gauge boson allow for a measurement of triple and quartic gauge
-couplings. They allow for a constraint of anomalous gauge couplings, where new physics might predominantly
+couplings. They can be used to constrain anomalous gauge couplings, where new physics might predominantly
 couple to electroweak gauge bosons. In this paper we chose a class of such processes where we consider two photons

### 2017-10-30 conclusions.tex
small modification

@@
 operators therefore requires the inclusion of higher order correction of both QCD as well as of the electroweak interaction.
+
 We also compared the two possibilities of combining QCD with electroweak corrections, namely either in an additive or
@@
 of neglected higher order contributions. We found that although this is true on the level of total cross sections there can be 
-regions in phase space where the leading order contribution vanishes and therefore the k-factor become infinitely large. 
+regions in phase space where the leading order contribution vanishes and therefore one or both $K$-factors become infinitely large. 
 For those kinematical edges we observe a breakdown of the multiplicative scheme whereas the additive scheme provides

### 2017-10-30 aaV_main.tex
preprint number, mention exp analysis for the cuts

@@
   \begin{flushright}
-    ZU--TH--??\\ CERN-TH-2017-226
+    ZU--TH 31/17\\ CERN-TH-2017-226
   \end{flushright}
@@
 $W$ or $Z$ boson. For the latter two cases we assume a leptonic decay of the boson. We calculate the next-to-leading
-order QCD and electroweak corrections to these processes with a particular emphasize on the until now unknown 
+order QCD and electroweak corrections to these processes with a particular emphasis on the until now unknown 
 electroweak corrections. We find that the electroweak corrections to the total cross section are moderate in the range of a few 
@@
  when combining
-QCD and electroweak corrections and we asess the importance of photon induced contributions to these processes. 
+QCD and electroweak corrections and we assess the importance of photon induced contributions to these processes. 
 }

### 2017-10-30 results.tex
preprint number, mention exp analysis for the cuts

@@
 bosons. 
-We define our fiducial phase space by the following. 
+We define our fiducial phase space by following experimental setups \cite{Aad:2015uqa}. 
 First, we require the presence of exactly one charged lepton, 
@@
 all non-resonant diagrams.
-The fiducial phase space of our analysis is defined as follows. 
+The fiducial phase space of our analysis is defined as follows, again according 
+to existing measurements \cite{Aad:2016sau}. 
 First, we require the presence of exactly one lepton pair 

### 2017-10-31 results.tex
minor mod
add description of both results w/ and w/o jet-veto in absolute plot

@@
     NLO EW (orange), NLO \QCDpEW\ (black) and NLO \QCDtEW\ (red) 
-    including scale uncertainties. The top ratio plot details 
+    including scale uncertainties. The top panel displays the 
+    absolute predictions for both the case with and without the 
+    application of a jet veto of $p_\mathrm{T,jet}^\mathrm{veto}=\text{30\,GeV}$, 
+    the latter ones are easily recognisable 
+    due to their much reduced rate. The top ratio plot details 
     the relative corrections to the leading order cross section 
-    without applying any jet veto, while the centre ratio plot 
-    applies a jet veto of $p_\mathrm{T,jet}^\mathrm{veto}=\text{30\,GeV}$. 
+    without applying the jet veto, while the centre ratio plot 
+    applies the jet veto. 
     The lower ratio highlights the size of the electroweak corrections.
@@
 the contributing diagrams. 
-
 Both the QCD and EW corrections are generally flat, taking 

### 2017-10-31 results.tex
corrected some typos

@@
 The use of a QCD-only PDF is justified by the fact that, 
-at LO, the photon induced corrections are either non-existant 
+at LO, the photon induced corrections are either non-existent 
 (\aaa, \aaw) or negligible (\aaz).
@@
 \ref{fig:aaz:dphi} that this situation is also present when one replaces one of the subleading
-photons by a $z$ boson. 
+photons by a $Z$ boson. 
 The electroweak corrections are negligible for this 
@@
 Nonetheless, they differ substantially between the three 
-oberservables and in their different regions. 
+observables and in their different regions. 
 While $\deltaQCD$ rises from values of 0.3 at small 
@@
 masses and increase as the invariant mass rises. 
-While $m_{\gamma_1\gamma_2}$ developes a correction 
+While $m_{\gamma_1\gamma_2}$ develops a correction 
 factor of $\deltaQCD=2$ at 200\,GeV and then falls 
@@
     photon as well as the dressed lepton pair (right) 
-    in diple photon production in association with a lepton pair 
+    in diphoton production in association with a lepton pair 
     at the LHC at 13\,TeV. 
@@
     photon and the lepton pair (right)
-    in diple photon production in association with a lepton pair 
+    in diphoton production in association with a lepton pair 
     at the LHC at 13\,TeV. 
@@
 Again, the QCD corrections are moderate, always staying below 
-$\deltaQCD=0.4$ and of a similar shape as encoutered already in 
+$\deltaQCD=0.4$ and of a similar shape as encountered already in 
 \aaw\ production. 
@@
 As discussed above this kinematic edge is also present in the case of the triple photon process
-(see Fig. \ref{fig:aaa:dphi_}) when considering the azimuthal angle between
+(see Fig. \ref{fig:aaa:dphi}) when considering the azimuthal angle between
 the leading and any subleading photon.

### 2017-10-31 setup.tex
corrected some typos

@@
 \ref{fig:aaa:amps}--\ref{fig:aaz:amps}. 
-The highest point loop integrals occuring in $\gamma\gamma\gamma$ 
+The highest point loop integrals occurring in $\gamma\gamma\gamma$ 
 production are pentagons, while both $\gamma\gamma e^-\bar\nu_e$ 

### 2017-10-31 results.tex
small addition

@@
 subleading photon and the lepton pair. 
-The familiar peak in $m_{\gamma_i\ell^+\ell^-}$ is produced by 
+The familiar peak in $m_{\gamma_i\ell^+\ell^-}$ at the $Z$ boson mass 
+is produced by 
 configurations where the respective photon is emitted by the 

### 2017-12-05 RefereeReply1.txt
corrections for points 8, 9, 10, 11 and 13 of referee report, added draft reply

We would like to thank the referee for his/her constructive and valuable 
comments.  The points raised clearly helped us to further improve the 
quality of the manuscript.  Below we give detailed replies to the referee's 
queries and indicate the corresponding adjustments or additions to the 
manuscript.  We thereby follow the referee's initial ordering: 
1) 
2)
3)
4)
5)
6)
7)
8)  The figure captions have been corrected.
9)  This has been rephrased to clearly state which particles the invariant 
    mass cut acts on.
10) The PDFs have been specified, and the respective publication referenced.
11) 
12) The description of the observables has been enhanced in the following 
    cases:
    - 
    - 
13) We agree and added a sentence stating exactly that.

We again would like to thank for the his/her feedback that clearly helped us to 
further improve the quality of the paper. We hope to have addressed all raised 
questions and suggestions such that the paper in its present form can be 
published in JHEP.

Sincerely yours

Nicolas Greiner, Marek Schoenherr

### 2017-12-05 results.tex
corrections for points 8, 9, 10, 11 and 13 of referee report, added draft reply

@@
   \caption{
-    Transverse momentum of the leading (left), subleading (centre) 
-    and third leading (right) photon at the LHC at 13\,TeV.
+    Transverse momentum of the leading (left) and subleading (centre) 
+    photon as well as the dressed lepton (right) in diphoton production 
+    in association with a lepton-neutrino pair at the LHC at 13\,TeV. 
+    Details as in Fig.\ \ref{fig:aaa:pt}.
     \label{fig:aaw:pt}
@@
     Pairwise invariant mass of the leading and subleading photon (left),
-    leading and third leading photon (centre), subleading and third leading 
-    photon (right) at the LHC at 13\,TeV.
+    the leading photon and the dressed lepton (centre), and the 
+    transverse mass of the $W$ boson (right)
+    in diphoton production in association with a lepton-neutrino 
+    pair at the LHC at 13\,TeV. 
+    Details as in Fig.\ \ref{fig:aaa:pt}.
     \label{fig:aaw:myy}
@@
     Azimuthal separation of the leading and subleading photon (left),
-    leading and third leading photon (centre), subleading and third leading 
-    photon (right) at the LHC at 13\,TeV.
+    the leading photon and the dressed lepton (centre), and the subleading 
+    photon and the dressed lepton (right)
+    in diphoton production in association with a lepton-neutrino pair 
+    at the LHC at 13\,TeV. 
+    Details as in Fig.\ \ref{fig:aaa:pt}.
     \label{fig:aaw:dphi}
@@
 size $R=0.1$, with $\pT>20\,\text{GeV}$ and $|\eta|<2.47$. 
-Their invariant mass must be larger than 40\,GeV. 
+The dressed lepton pair invariant mass must be larger than 40\,GeV. 
 As in the case of \aaw production, we then require at least 
@@
 to be $\Delta R(\gamma_1,\gamma_2)>0.4$ and each photon and 
-the lepton to be $\Delta R(\ell,\gamma)>0.4$.
+each lepton to be $\Delta R(\ell,\gamma)>0.4$.
 The inclusive cross sections and correction factors were 
@@
 Figure \ref{fig:aaz:aa-ind}. 
+\revised{To ensure that the quark and gluon PDFs are as close as 
+possible to our nominal set, they are calculated using the CT14nlo 
+QED \cite{Schmidt:2015zda} set, including both an elastic and an 
+inelastic (with an intrinsic photon momentum fraction of 
+$p_0^\gamma=0.005$) component.}
 The photon-induced contribution is typically a few per mille of the 
@@
 by tightening the acceptance window in the lepton-pair invariant mass.
+\revised{Following \cite{Denner:2015fca}, the $\gamma q$- and 
+$\gamma\bar{q}$-induced channels at NLO EW are expected to contribute 
+less than the $\gamma\gamma$ channels, both with and without a jet veto. 
+They can thus be safely neglected here as well. 
+The same reasoning also applies to \aaw\ production, 
+cf.\ \cite{Denner:2014bna}.}

### 2017-12-05 RefereeReply1.txt
slightly improved figs, added comment to paper and ref reply

@@
 4)
-5)
+5)  We have somewhat improved the plots to better distinguish the 
+    results with and without a jet veto. The caption of Fig. 1 is 
+    amended accordingly.
 6)

### 2017-12-05 results.tex
slightly improved figs, added comment to paper and ref reply

@@
     including scale uncertainties. The top panel displays the 
-    absolute predictions for both the case with and without the 
+    absolute predictions for both the case with \revised{(dashed)} and without \revised{(solid)} the 
     application of a jet veto of $p_\mathrm{T,jet}^\mathrm{veto}=\text{30\,GeV}$, 

### 2017-12-05 RefereeReply1.txt
corrected bib, added reply to 6) and 7)

@@
 5)  We have somewhat improved the plots to better distinguish the 
-    results with and without a jet veto. The caption of Fig. 1 is 
-    amended accordingly.
-6)
-7)
+    results with and without a jet veto. The caption of Fig. 4 is 
+    amended accordingly. The focus, however, is on the ratios where 
+    only a subset of results is plotted and legibility is, in our 
+    estimation, sufficient for the points raised in the manuscript.
+6)  As detailed in the manuscript in the paragraph above eq. (3.3), 
+    we compute the LO result including its factorisation scale 
+    uncertainty, and the EW correction factor for the central scale 
+    choice. The NLO EW result, according to eq. (3.3) thus carries 
+    the LO factorisation scale uncertainty.
+    As labeled, the plots themselves show not delta-EW, which we compute only 
+    for the central scale choice, but the full NLO EW result exhibiting 
+    the LO factorisation scale uncertainty. In the ratios the NLO EW 
+    result in relation to the central LO prediction is shown, i.e. 
+    the resulting uncertainty band has the same relative size as 
+    the LO uncertainty band.
+    We have amended the caption of Fig. 4 to explicitly reflect 
+    the reference of the ratio plots.
+7)  We have rendered this statement more precise and hope that it 
+    is clear now.
 8)  The figure captions have been corrected.

### 2017-12-05 results.tex
corrected bib, added reply to 6) and 7)

@@
     The lower ratio highlights the size of the electroweak corrections.
+    \revised{All ratios are taken with respect to the LO prediction 
+    using out central scale choice.}
     \label{fig:aaa:pt}
@@
 uncertainty estimate.
-Due to the different sizes of the QCD and electroweak 
-corrections, the additive and multiplicative combination 
-of corrections lead to very similar results.
+Due to the different sizes of QCD and electroweak 
+corrections, \revised{$\deltaQCD\gg\deltaEW$,} the additive and multiplicative combination 
+of corrections lead to very similar results 
+\revised{as $\deltaQCD\deltaEW\ll\deltaQCD$}.
 

### 2017-12-05 RefereeReply1.txt
worked on points 1-4 in referee report, added reference

--- 2017-12-05 RefereeReply1.txt
@@
 manuscript.  We thereby follow the referee's initial ordering: 
-1) 
-2)
-3)
-4)
+1) The use of alpha(0) is motivated by the real emission that takes place at
+   q^2=0. In order to obtain pole cancellation between the reals and the virtuals
+   we chose the same factor for the virtual contribution. We are aware that there
+   are other valid choices, however, at least in this case, the differences are small
+   compared to the genuine electroweak corrections. We added a corresponding sentence
+   about the motivation of the choice to the draft.
+2) Renormalization- and factorization scale have been varied indepedently from 1/2 to 2 within 
+   a 7 point scale variation, i.e. the combinations 0.5/2 and 2/0.5 are not present. The scale
+   uncertainty has then be determined by the envelope of the various results.
+   We added this information to the draft.
+3) We added a sentence stating this explicitly.
+4) The only analysis for three or more photons (Ref 6) focusses on heavy intermediate BSM
+   particles. Therefore it did not make sense to adopt this set of cuts and we rather used generic
+   cuts similar to the one applied for diphoton searches (i.e. asymmetric cuts between 1st and
+   2nd photon). But they are not according to a specific experimental analysis. Nevertheless 
+   they have been chosen in such a way that they are likely to be similar/comparable to a possible
+   experimental analysis.
 5)

### 2017-12-05 results.tex
worked on points 1-4 in referee report, added reference

@@
 The additional power of $\alpha$ in the NLO EW correction 
-is evaluated in \alphazero-scheme again.
+is evaluated in \alphazero-scheme again. \revised{This choice is motivated by the fact
+that the real emission contribution takes place at $q^2=0$ and in order to obtain
+pole cancellation between the real emission contribution and the virtual corrections we
+chose the same factors in both contributions. An alternative choice would be to use
+the \Gmu-scheme throughout.}
 The virtual amplitudes are renormalised correspondingly.
@@
 by the conventional factor of two around their central values 
-$\muR^0$ and $\muF^0$, respectively.
+$\muR^0$ and $\muF^0$, respectively. \revised{ $\muR$ and $\muF$ are
+varied independently within a 7-point scale variation, i.e. the 
+two cases where one scale is the inverse of the other scale is not present.
+The uncertainty bands shown later in the various distributions are given
+by the envelope of these 7 results. It should be noted that the QCD scale variation is
+completely unrelated to the electroweak corrections. Nevertheless it is interesting
+to compare the two as it is the general assumption the the LO QCD scale uncertainty
+covers all higher order effect. Therefore it is interesting and important to investigate
+whether this assumption is true. }
 We do not vary the factorisation scale for the determination 

### 2017-12-05 setup.tex
worked on points 1-4 in referee report, added reference

@@
 NLO QCD corrections to $ZZ+\text{jet}$, $t\bar{t}+0,1\,\text{jets}$, 
-$W^{+}W^{-}b\bar{b}$ and $h+0,1,2,3\,\text{jets}$ production 
+$W^{+}W^{-}b\bar{b}$, $h+0,1,2,3\,\text{jets}$  and $\gamma\gamma b \bar{b}$ production 
 in \cite{Binoth:2009wk,Hoeche:2013mua,Heinrich:2013qaa,
-  Greiner:2015jha,Greiner:2016awe,Heinrich:2017bqp} and the 
+  Greiner:2015jha,Greiner:2016awe,Heinrich:2017bqp,Faeh:2017fpp} and the 
 NLO EW corrections to $\gamma\gamma+0,1,2\,\text{jets}$ production 

### 2017-12-05 results.tex
slightly modified in-text addition to 1) and moved it to footnote not to spoil the flow of the argument

@@
 While we calculate triple photon production in the \alphazero-scheme, 
-we use a mixed scheme for \aaw\ and \aaz production: at LO two 
+we use a mixed scheme for \aaw\ and \aaz\ production: at LO two 
 powers of $\alpha$ are taken in the \alphazero-scheme, while 
@@
 The additional power of $\alpha$ in the NLO EW correction 
-is evaluated in \alphazero-scheme again. \revised{This choice is motivated by the fact
+is evaluated in \alphazero-scheme again. \footnote{\revised{This choice is motivated by the fact
 that the real emission contribution takes place at $q^2=0$ and in order to obtain
@@
 chose the same factors in both contributions. An alternative choice would be to use
-the \Gmu-scheme throughout.}
+the \Gmu-scheme for the NLO correction as well. This choice is tailored towards an 
+improved description of the weak part of the electroweak correction. Although 
+the difference of both schemes is beyond the accuracy of the present analysis, 
+both schemes are easily converted from one into the other as 
+$\deltaEW\propto\alpha$.
+Thus, the electroweak corrections are a relative 3.7\% larger in this scheme.}}
 The virtual amplitudes are renormalised correspondingly.
@@
 to compare the two as it is the general assumption the the LO QCD scale uncertainty
-covers all higher order effect. Therefore it is interesting and important to investigate
+covers all higher order effects. Therefore it is interesting and important to investigate
 whether this assumption is true. }
@@
     \revised{All ratios are taken with respect to the LO prediction 
-    using out central scale choice.}
+    using the central scale choice.}
     \label{fig:aaa:pt}
@@
 The dressed lepton pair invariant mass must be larger than 40\,GeV. 
-As in the case of \aaw production, we then require at least 
+As in the case of \aaw\ production, we then require at least 
 two identified photons among the remaining ones after dressing, 
@@
 The first observation is, while the general behaviour of the 
-spectra is the same as in \aaw production, the inclusive QCD 
+spectra is the same as in \aaw\ production, the inclusive QCD 
 corrections are much smaller in this case. 
@@
 The electroweak corrections, on the other hand, are qualitatively very similar 
-to the \aaw case: with the exception of the well known positive 
+to the \aaw\ case: with the exception of the well known positive 
 radiative corrections below the $Z$ peak, they are negative 

### 2017-12-06 RefereeReply1.txt
point 12

@@
     cases:
-    - 
-    - 
+    - Figure 6
+    - Figures 8,11
 13) We agree and added a sentence stating exactly that.

### 2017-12-06 results.tex
point 12

@@
 and NLO EW corrections relax the kinematic boundaries of 
-the leading order calculation. 
-Especially the azimuthal separation of the leading and 
+the leading order calculation.Especially the azimuthal separation of the leading and 
 third leading photon receives substantial shape corrections 
@@
 minimal distance the second photon can have to the leading one.  Only at NLO where
-one can have additional radiation this constraint is relaxed. We will see later in Fig.
+one can have additional radiation this constraint is relaxed. 
+\revised{Therefore on finds that for the distributions involving the leading photon the particles
+tend to be in a back-to-back configuration. This is most pronounced for the separation between
+the two hardest photons and gets step by step relaxed by replacing the subleading by the third leading
+photon and the leading by the subleading respectively.} We will see later in Fig.
 \ref{fig:aaz:dphi} that this situation is also present when one replaces one of the subleading
@@
 the LO uncertainty estimate and play an important 
-role.
-
+role. \revised{The change of shape due to the QCD corrections is
+different compared to the three photon case where the QCD corrections 
+are largest for small invariant masses and then continuously decrease with
+higher masses. Due to the presence of a heavy gauge boson additional radiation
+shifts the invariant mass towards higher values.}
 Figure \ref{fig:aaw:myy} also displays the transverse 
@@
 of the leading and subleading photon, and both the leading and 
-subleading photon and the lepton pair. 
+subleading photon and the lepton pair. \revised{For the invariant mass of the
+two leading photons one also observes a shift towards higher invariant masses
+in the presence of QCD corrections as seen in Fig. \ref{fig:aaw:myy}. The effect
+is less pronounced due to the fact that there is also a triple photon process contributing
+to the dilepton final state. The observed pattern is therefore a mixture between what
+can be seen in Fig. \ref{fig:aaa:myy} and the results in Fig. \ref{fig:aaw:myy}.}
 The familiar peak in $m_{\gamma_i\ell^+\ell^-}$ at the $Z$ boson mass 

### 2017-12-18 RefereeReply1.txt
updated referee reply

--- 2017-12-05 RefereeReply1.txt
@@
 10) The PDFs have been specified, and the respective publication referenced.
-11) 
+11) Added reference to 1412.7421 and 1510.08742
 12) The description of the observables has been enhanced in the following 
     cases:
-    - 
-    - 
+    - Figure 6
+    - Figures 8,11
 13) We agree and added a sentence stating exactly that.

### 2017-12-21 RefereeReply1.txt
completed ref reply

@@
    experimental analysis.
-5)
-6)
-7)
+5) We have slightly improved the readability of the plots by adopting 
+   dashed line styles for the jet vetoed NLO QCD prodictions and their 
+   derivatives. The main focus, however, is on the ratio plots where 
+   the lines lines are fewer and better to differentiate. The absolute 
+   plot only serves to give the order of magnitude of the respective 
+   cross sections.
+6) The scales are determined by building an envelope around the 
+   variation of the scaledependences detailed between eq. (3.2) and 
+   (3.3). The ratio is then taken with respect to the central LO 
+   prediction. "Hence, our NLO EW results exhibits the exact same 
+   muF-dependence as the LO result", as is stated in the text directly 
+   above eq. (3.3).
+7) We have completed the sentence with mathematical relations of the sizes 
+   of the QCD and EW corrections, it should be much clearer now.
 8)  The figure captions have been corrected.

### 2017-12-22 RefereeReply1.txt
updated reference and reply

@@
    cross sections.
-6) The scales are determined by building an envelope around the 
-   variation of the scaledependences detailed between eq. (3.2) and 
-   (3.3). The ratio is then taken with respect to the central LO 
-   prediction. "Hence, our NLO EW results exhibits the exact same 
-   muF-dependence as the LO result", as is stated in the text directly 
-   above eq. (3.3).
+6) The scales uncertainties are determined by building an envelope 
+   around the variation of the scale dependences detailed between 
+   eq. (3.2) and (3.3). The ratio is then taken with respect to the 
+   central LO prediction. "Hence, our NLO EW results exhibits the 
+   exact same muF-dependence as the LO result", as is stated in the 
+   text directly above eq. (3.3). A sentence detailing this has also 
+   been added to the caption of Fig. 4. In that sense, we do not 
+   plot the electroweak correction as such, but the whole NLO EW 
+   prediction, as the plot labels suggest.
 7) We have completed the sentence with mathematical relations of the sizes 

### 2017-12-22 setup.tex
updated reference and reply

@@
   Dittmaier:1999mb,Gleisberg:2007md,Kallweit:2014xda,
-  Kallweit:2015dum,Kallweit:2017khh,Schonherr:2017xxx}
+  Kallweit:2015dum,Kallweit:2017khh,Schoenherr:2017xxx}
 and includes the appropriate initial state mass factorisation 

### 2017-12-22 results.tex
update on bib and typos

@@
 one can have additional radiation this constraint is relaxed. 
-\revised{Therefore on finds that for the distributions involving the leading photon the particles
+\revised{Therefore, one finds that for the distributions involving the leading photon the particles
 tend to be in a back-to-back configuration. This is most pronounced for the separation between
@@
 two leading photons one also observes a shift towards higher invariant masses
-in the presence of QCD corrections as seen in Fig. \ref{fig:aaw:myy}. The effect
+in the presence of QCD corrections as seen in Fig.\ \ref{fig:aaw:myy}. The effect
 is less pronounced due to the fact that there is also a triple photon process contributing
 to the dilepton final state. The observed pattern is therefore a mixture between what
-can be seen in Fig. \ref{fig:aaa:myy} and the results in Fig. \ref{fig:aaw:myy}.}
+can be seen in Fig.\ \ref{fig:aaa:myy} and the results in Fig.\ \ref{fig:aaw:myy}.}
 The familiar peak in $m_{\gamma_i\ell^+\ell^-}$ at the $Z$ boson mass 
